### 2017-04-20 paper.tex
Initial commit. Converting from existing progress report to Latex.

\documentclass[10pt,journal]{IEEEtran}
\usepackage[
  backend=biber,
  style=alphabetic,
  citestyle=numeric
]{biblatex}
\addbibresource{citations.bib}
\begin{document}
\title{Capture and Replay Tools in the Field}
\author{Deepa Chhetri and Brian Pollack}
\maketitle

\begin{abstract}
TODO: Abstract
\end{abstract}

\section{Introduction}

\IEEEPARstart{S}{oftware} testing is a process of  evaluating the software for its functionality by performing some test cases on an attribute or capability of a program or system and determining that it meets its required results. Software testing involves the execution of a software component or system component to evaluate one or more properties of interest. Testing the graphical user interface (GUI) of a software product is important to ensure the quality of the system and therefore to improve the user satisfaction of using the software\cite{Nedyalkova:2013:OSC:2494444.2494464}. But testing GUI is tedious and time consuming because it requires a sequence of user interactions. There are special tools available to test such software. These tools are called capture and replay tools. They capture a sequence of interactions which can be replayed at a later time for testing.

\section{Previous Work}
Nedyalkova and  Bernardino established a comparison of capture and replay tools. They evaluated five open source capture and replay tools namely Abbot, Jacareto, JFCUnit, Marathon and Pounder. The criteria that they used for comparison is divided into two major groups - ``General Characteristics'' and ``Capture/Replay Characteristics''. General characteristics include:
\begin{enumerate}
\item Easy to Install
\item User Interface
\item Easy to Use
\item Easy to Launch Application Under Test (AUT)
\item Documentation
\item Tutorials
\item Examples
\item Programming Skills Required
\end{enumerate}
Capture/Replay Characteristics include:
\begin{enumerate}
\item Text Field - interaction with a JTextField
\item Mouse Move - detection of mouse movements on a component
\item Mouse Drag - detection of mouse drags
\item Mouse Clicks - detection of mouse clicks
\item Component - interaction with a window
\item Scrolling - interaction with the scrollbar of a JTextArea
\item File Dialog - navigating the directories in a JFileChooser
\item Combo Box - selecting an item in a JComboBox
\end{enumerate}
Based on the results, they found out that Jacareto is the best tool among all five evaluated. Jacareto is easy to install, had better documentation, does not require additionally programming skills, supports all capture and replay characteristics except for navigation of dialog box. It allows tester to replay the test script in a speed that facilitates to observe the actions \cite{Nedyalkova:2013:OSC:2494444.2494464}.

Similarly, Rodrigues et al. performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools. They studied the effort required (time spent) to use CR-based and MBT tools. They compared LoadRunner and Visual Studio CR-based tools and the PLeTsPerf MBT tool to create performance test scripts and scenarios to test web applications. LoadRunner (LR) is a performance testing tool based on the CR technique that supports scripts generation and execution to test Web-based applications. Visual Studio (VS) [3] is an IDE developed by Microsoft to support software design, development and test. PLeTsPerf(PP) is a model-based performance testing tool. Rodrigues et al. used used an in-vitro approach, since it refers to the experiment in the laboratory under controlled conditions, addressing a real problem, i.e., the differences in individual effort to create performance test scripts and scenarios using LR,VS and PP. They performed the experiment to answer three research questions (RQ) - RQ1. What is the effort to generate a single performance test script and scenario using PP, LR, and VS? RQ2. What is the effort to re-generate performance test scripts and scenarios when using PP, LR, and VS? RQ3. What is the effort to generate a set of performance test scripts and scenarios using PP, LR, and VS? The experiment execution phase was split into three sessions, each composed of three tasks. These tasks were performed using the PP, LR  and VS approaches, one for each task, and all tasks should generate an equivalent performance test script as an output. They summarize the result by giving average time spent per treatment to complete each session. They found out that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly \cite{Rodrigues:2014:ECR:2652524.2652587}.

Mugshot is a deterministic capture and replay tool developed by Microsoft. It captures every event in  that is executed in JavaScript program which can be replayed deterministically at any later time to analyze the sequence of events that might have led to system failure. To capture application activity, it records all sources of nondeterminism. If an application is run again and injected with the same non deterministic events, the program will follow the same execution path that was observed at logging time. It has its client side implemented in JavaScript to easily record logs instead of downloading additional plug-ins. For each new event it captures, it creates a log entry that contains a sequence number and wall clock time. The entry also contains the event type and enough type-specific data to recreate event at play time. Mugshot uses a caching proxy to reproduce the load events in the log \cite{Mickens:2010:MDC:1855711.1855722}. This is the limitation of Mugshot. If an application fetches external contents that does not pass through the proxy, Mugshot cannot guarantee faithful replay of its data or its load time.

\section{Description of Capture and Replay Tools Used}
\subsection{Reanimator}
Reanimator\footnote{https://github.com/WaterfallEngineering/reanimator} captures non-deterministic input to a JavaScript application in a log that can replayed at a later date. It was originally designed for recording web application crashes in the wild for later debugging. It is inspired by Microsoft’s Mugshot. It is built on JQuery 1.8.3. The code for Reanimator is available on GitHub and is under MIT license. It works only on Firefox. It supports both Windows and Linux platforms.

\subsection{Sahi}
Sahi\footnote{http://sahipro.com/} is an Automation testing tool that is used for testing web application. There are two versions of Sahi tool: one is open source and is available on SourceForge and proprietary version called Sahi Pro which is available on their official website. Open source comes with basic record and replay functionalities written in Java and JavaScript. It works on Internet Explorer, Firefox and Chrome. It only supports Windows platform.

\subsection{Telerik}
Telerik Test Studio\footnote{http://www.telerik.com/teststudio} is commercial windows-based software testing tool with Visual Studio plugins. It facilitates web and desktop (GUI) functional testing, performance testing and mobile app testing with Record and Replay features. It supports JavaScript, HTML, ASP.NET, Ajax, Silverlight etc and facilitates quick validations. It works on Internet Explorer, Firefox, Chrome and Safari.

\subsection{Selenium IDE}
Selenium IDE\footnote{http://www.seleniumhq.org/projects/ide/}: Selenium is known as umbrella project that enables web browser testing for all browsers. It is a open source free application supports GUI Testing and web functional testing. It is implemented as a Firefox extension, and allows recording, editing, and debugging tests. It includes the entire Selenium Core which allows easy and quick record and play back tests in the actual environment that they will run in. It supports both Windows and Linux platforms.

\section{Evaluation of Existing Tools}
We focused on capture and replay tools that are built for internet applications. Here, we compared four tools – Reanimator, Sahi, Telerik and Selenium IDE. The tools are installed on an HP laptop with Intel core i5 processor (2.30 GHz), 4 GB RAM and windows 8.1 operating system with Java 1.8. We installed the tools Sahi, Telerik and Selenium. The code for Reanimator was directly deployed on a web server we manage.
The following criteria are used to establish comparison between these tools:
\begin{enumerate}
\item Easy to install
\item Time required to install
\item User interface
\item Tutorials available
\item Open source
\item Programming skills required
\item Documentation provided
\item Examples provided
\item User interface for developers
\end{enumerate}
Level of detail of measurements:
\begin{enumerate}
\item Interaction with text fields
\item Mouse movements
\item Mouse clicks
\item Mouse drags
\item Scrolling
\item Dialog box
\end{enumerate}
System Information:
\begin{enumerate}
\item Size
\item Platforms
\item Browser support
\item Additional features
\end{enumerate}

\printbibliography

\end{document}

### 2017-04-21 paper.tex
Added more text that was in our progress report

@@
-\documentclass[10pt,journal]{IEEEtran}
+\documentclass[12pt,journal]{IEEEtran}
 \usepackage[
   backend=biber,
-  style=alphabetic,
+  style=numeric,
   citestyle=numeric
@@
 \addbibresource{citations.bib}
+\usepackage{pifont}
 \begin{document}
@@
 
+\begin{table*}[b]
+\centering
+\begin{tabular}{ | c | c | c | c | c | }
+\hline
+Characteristic            & Reanimator  & Sahi  & Telerik & Selenium IDE \\
+\hline
+Easy to Install           & X & \ding{51} & \ding{51} & \ding{51} \\
+\hline
+Time Required to Install  & Very Quick & Quick & Very Long and Tedious & Quick \\
+\hline
+User Interface            & X & \ding{51} & \ding{51} & \ding{51} \\
+\hline
+Easy to Use               & X & \ding{51} & \ding{51} & \ding{51} \\
+\hline
+Documentaion              & X & \ding{51} & \ding{51} & \ding{51} \\
+\hline
+Tutorial                  & X & X & \ding{51} & \ding{51} \\
+\hline
+Open Source               & \ding{51} & \ding{51} & X & \ding{51} \\
+\hline
+Examples                  & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
+\hline
+Programming Skills        & \ding{51} & X & X & X \\
+\hline
+
+\end{tabular}
+\caption{Caption.}
+\end{table*}
+
+\begin{table*}[b]
+\centering
+\begin{tabular}{ | c | c | c | c | c | }
+\hline
+Characteristic            & Reanimator  & Sahi  & Telerik & Selenium IDE \\
+\hline
+Mouse Click               & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
+\hline
+Text Field                & X & \ding{51} & \ding{51} & \ding{51} \\
+\hline
+Mouse Drags               & X & X & X & X \\
+\hline
+Mouse Move                & X & X & X & X \\
+\hline
+Scrolling                 & X & X & X & X \\
+\hline
+Dialog Box                & X & \ding{51} & \ding{51} & \ding{51} \\
+\hline
+
+\end{tabular}
+\caption{Caption.}
+\end{table*}
+
+\section{Comparison Analysis}
+All the tools are good at capturing and replaying task.
+But while taking other criteria into consideration, Sahi performs better than the other tools.
+It has very easy and quick installation.
+It has very well documentation and tutorials available online.
+It does not require any programming skill to use Sahi.
+Selenium also provides all these features but it can only be used to capture and replay Firefox sessions.
+It allows the user to set speed to analyse the scenarios.
+Telerik has a major setback that its installation takes very long (it took us 1 day to install) to finish since it requires lot of dependencies and also its installation process is not very effective.
+It requires large hard disk space.
+It has the feature called storyboard which is the snapshot of each scenario.
+Reanimator is a small capture and replay tool inspired by Mugshot.
+It requires programming skills since it does not come as ready to use testing tool.
+It is built on JQuery 1.8.3 and works only on Firefox.
+In our further work, we upgraded it to JQuery 3.2.0 and enabled it to work on Chrome too.
+
+\section{Extension and Modification of Reanimator}
+We forked the original Reanimator GitHub project at https://github.com/brianmpollack/reanimator.
+It took awhile to determine exactly how the original authors built Reanimator, but we were able to understand their work update their code to work with JQuery 3.2.0, the current version.
+
+While updating the Reanimator code, we learned why it did not initially work in Google Chrome.
+It appears that the original authors tried to convert DOM objects to JSON.
+It is commonly known that JSON does not support circular references, but DOM objects contain numerous circular references.
+Some browsers, such as Firefox, will simply proceed with the JSON encoding and dropped the circular references, but other browsers, such as Chrome, will terminate the JavaScript process.
+We found a simple function that will remove the circular references from the DOM object and convert it to JSON, allowing Reanimator to now be used in any major browser.
+It needs testing on browsers such as Internet Explorer and Edge, but it worked in our preliminary tests with Firefox, Chrome, and Safari.
+
+We also found a file error in the included demos.
+The original Makefile added a symbolic link to link the Reanimator JavaScript code to the demos, but the symbolic link caused issues both when all the code is uploaded to GitHub and even locally on my computer.
+For now, we simply copied the correct files into position on our web server, but we plan to update the Makefile to copy the files automatically.
+We are saving this for the end of the project because we anticipate having many changes to make to the demos (to reflect our new features/code), so we will update the demos all at once.
+
 \printbibliography

### 2017-04-24 caption/issues/04-12-19-dctt.tex
added caption package, figures and edited paper

\documentclass[12pt,a4paper]{scrartcl}
\usepackage{ngerman}
\usepackage[latin1]{inputenc}
\usepackage[font=small]{caption}[2004/07/16]

\begin{document}
\begin{figure}
  \centering
  \caption{Dies ist ein Text, der nur zu Testzwecken eingefügt ist, um die
    Zeilenabstände sichtbar zu machen.  Hier taucht jetzt ein \AA{}
    auf, an dem aufgezeigt werden soll, dass eben die Zeilenabstände nicht
    stimme.  Und noch mehr Text taucht hier auf, damit auch gesichert
    mindestens vier Zeilen in dem fertigen Dokument stehen.}
\end{figure}
\end{document}

### 2017-04-24 caption/issues/05-11-30-email.tex
added caption package, figures and edited paper

\documentclass[letterpaper,11pt,oneside,pdftex]{article}
\usepackage[demo]{graphicx}
\usepackage{rotating}
\usepackage{caption}

\begin{document}

\noindent
The following commands
\begin{verbatim}
     \begin{figure}[!ht]
       \centering
       \begin{minipage}[c]{3cm}
          \hfill\includegraphics[width=4cm,angle=90]{graphic}
       \end{minipage}%
       \hspace{20pt}%
       \begin{minipage}[c]{30pt}
          % \captionsetup{width=4cm}
          \rotcaption{Rotcaption Caption}
          \label{fig:rotcaption}
       \end{minipage}
     \end{figure}
\end{verbatim}
produce Figure~\ref{fig:rotcaption}.

     \begin{figure}[!ht]
       \centering
       \begin{minipage}[c]{3cm}
          \hfill\includegraphics[width=4cm,angle=90]{graphic}
       \end{minipage}%
       \hspace{20pt}%
       \begin{minipage}[c]{30pt}
          % \captionsetup{width=4cm}
          \rotcaption{Rotcaption Caption}
          \label{fig:rotcaption}
       \end{minipage}
     \end{figure}

Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.

Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.

Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.

Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.

Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.

Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.
Text text text text text text text text text text text text text text.

\end{document}

### 2017-04-24 caption/issues/06-05-31-ctt.tex
added caption package, figures and edited paper

\documentclass{article}

\usepackage{caption}
\usepackage{subfig}
\usepackage{chngpage}

\listfiles

\begin{document}

\section{Hello}

This is one paragraph of text.
Foo foo foo foo foo foo foo foo.

\begin{figure}[t]
  \begin{adjustwidth}{-2cm}{-2cm}
  \centering
  \subfloat[One subcaption. Let's make this subcaption a bit longer.]{%
    \label{fig:example_one_a}%
    \parbox{7cm}{One one one one one one one one one one one one one one one one.}%
  }%
  \qquad
  \subfloat[Another subcaption.]{%
    \label{fig:example_one_b}%
    \parbox{7cm}{Two two two two two two two two two two two two two two two two.}%
  }
  \caption{The main caption is here.}%
  \label{fig:example_one}%
  \end{adjustwidth}%
\end{figure}

This is also one paragraph of text to conclude this example, see Figure~\ref{fig:example_one}.
Bar bar bar bar bar bar bar bar.

\begin{figure}[b]
  \centering
  \subfloat[One subcaption. Let's make this subcaption a bit longer.]{%
    \label{fig:example_two_a}%
    \parbox{5cm}{One one one one one one one one one one one one one one one one.}%
  }%
  \qquad
  \subfloat[Another subcaption.]{%
    \label{fig:example_two_b}%
    \parbox{5cm}{Two two two two two two two two two two two two two two two two.}%
  }
  \caption{The main caption is here.}%
  \label{fig:example_two}%
\end{figure}

\end{document}

### 2017-04-24 caption/issues/07-09-13b-mrunix.tex
added caption package, figures and edited paper

\iffalse
http://www.mrunix.de/forums/showthread.php?t=53862
Neues Caption Paket verträgt sich nicht mit Koma Klassen?
Hallo
Seit ich das neuste Caption Paket v3.1 mit den KOMA-Script package v.2.97a benutze, bekomme ich die Fehlermeldung:

"Something's wrong -- perhaps a missing \item"

Dies nur dann, wenn ich beim Caption Paket die Optionen justification=centering,labelsep=newline kombiniere und die Caption so lange ist, dass sie automatisch auf mehrere Zeilen umbricht.

Hier mal ein Minimalbeispiel:
Code:
\fi

\documentclass[12pt, nochapterprefix, BCOR0mm]{scrreprt}
\usepackage[justification=centering,labelsep=newline]{caption}
\begin{document}
test
\begin{figure}
	\caption{sehr langer text sehr langer text sehr langer text sehr langer text sehr langer text sehr langer text}
\end{figure}			
\end{document}

Weiter scheint es so, dass beim Weglassen der Option justification=centering zwar keine Fehlermeldung mehr erscheint, die Option labelsep=newline aber unwirksam ist.

Ich möchte nun aber, dass das Label der Beschriftung auf einer Zeile steht und darunter (im Idealfall zentriert) die Beschreibung.
Kann mir jemand weiterhelfen?

Besten Dank!
__________________
Grüsse

Thomas

### 2017-04-24 caption/issues/07-09-17b-mrunix.tex
added caption package, figures and edited paper

\iffalse
http://www.mrunix.de/forums/showthread.php?t=53862
Hi Axel
Hab zwar caption 3.1a noch nicht drauf, aber ich hab rausgefunden, woran es vorher lag. Anscheinend verursacht \centering innerhalb der figure Umgebung den Fehler. Hier ein Minimalbeispiel:
Code:
\fi

\documentclass{scrreprt}
\usepackage[format=plain,labelsep=newline]{caption}
\begin{document}
test
\begin{figure}
	\centering
	\caption{sehr langer text sehr langer text sehr langer text sehr langer text sehr langer text sehr langer text}
\end{figure}			
\end{document}

Werde jetzt dann dein neues Packet drauf tun und schauen, ob sich was tut.

Grüsse

Thomas

### 2017-04-24 caption/issues/07-11-09-ctt.tex
added caption package, figures and edited paper

\iffalse
Date: Fri, 09 Nov 2007 22:19:11 +0100
From: =?UTF-8?B?IkNocmlzdGlhbiBFLiBCw7ZobWUi?= <hacks@cb8_replace_with_dot_org>
Organization: Wouldn't you like to know ?!!
User-Agent: Mozilla/5.0 (X11; U; Linux ppc; en-US; rv:1.8.0.13pre) Gecko/20070505 Iceape/1.0.9 (Debian-1.0.10~pre070720-0etch3+lenny1)
Newsgroups: comp.text.tex
Subject: figures, captions and skips
Message-ID: <4734cee5$0$13123$9b4e6d93@newsspool2.arcor-online.net>

Hi all,

while including figures/images of various widths, I noticed
that within the figure environment apparently the space/skip
generated between the caption and the included image changes
proportionally to the width of the image being included.  To
be precise, I would expect the code

\documentclass{book}

...

\usepackage{graphicx}
\usepackage{caption}
\captionsetup{position=bottom,font=small,labelfont=bf,format=hang}
\usepackage{subfig}

...

\begin{figure}
\centering
\includegraphics[keepaspectratio=true]{the-image.pdf}
\captionsetup{aboveskip=1em,belowskip=1em}
\caption[the title]{the caption}
\end{figure}

to place a caption below the image (which is assumed to be of
\textwidth width) using the same aboveskip amount that is being
generated for an image of half that width.  However, the code

...

\begin{figure}
\centering
\subfloat[][]{\includegraphics[keepaspectratio=true]{the-image.pdf}}
\captionsetup{aboveskip=1em,belowskip=1em}
\caption{...}
\end{figure}

...

does produce the intended aboveskip but with the drawback of a
subnumber on a one image figure which is somewhat undesirable.
Setting the global \abovecaptionskip had the same effect as
\captionsetup{aboveskip=1em}, ie, only producing an offset
bt not an absolute distance.

Is there a way to unconditionally/globally set the aboveskip
for a caption of a figure to a value that remains constant for
all images irrespective of their dimension ?

Thanks and regards,
Christian Boehme
\fi

\documentclass{book}

%...

\usepackage[demo]{graphicx}
\usepackage{caption}
\captionsetup{position=bottom,font=small,labelfont=bf,format=hang}
%\usepackage{subfig}

%...

\begin{document}

\begin{figure}
\centering
\includegraphics[keepaspectratio=true,width=0.5\linewidth]{the-image.pdf}
\captionsetup{aboveskip=1em,belowskip=1em}
\caption[the title]{the caption}
\end{figure}

\begin{figure}
\centering
\includegraphics[keepaspectratio=true,width=0.7\linewidth]{the-image.pdf}
\captionsetup{aboveskip=1em,belowskip=1em}
\caption[the title]{the caption}
\end{figure}

\begin{figure}
\centering
\includegraphics[keepaspectratio=true,width=1.0\linewidth]{the-image.pdf}
\captionsetup{aboveskip=1em,belowskip=1em}
\caption[the title]{the caption}
\end{figure}

\end{document}

### 2017-04-24 caption/issues/08-03-21.tex
added caption package, figures and edited paper

% This error was found by myself on 2008-03-21:

% Translate to PDF!
% (Fixed with ltcaption.sty v1.1b)
\documentclass[pdftex]{article}
\usepackage{caption,longtable}
\usepackage[verbose]{hyperref}
%\ifpdf\usepackage{hypdestopt}\fi

\begin{document}
\section{Test}

\noindent This one works without hyperref warning (and gives a correct jump to the footnote):
\begin{longtable}{ll}
A & B~\footnotemark\\
\end{longtable}
\footnotetext{Huba!}

\noindent And this not:
\begin{longtable*}{ll}
A & B~\footnotemark\\
\end{longtable*}
\footnotetext{Huba!}

\clearpage
A

\end{document}

Mit "longtable":
pdftex: define anchor at line 8: section.1
pdftex: bookmark at 8: {1}{\ifnum 1>\c@secnumdepth \else \protect \numberline {
\csname thesection\endcsname }\fi Test}{section.1}{1}{toc}
pdftex: define anchor at line 12: table.1
pdftex: define anchor at line 13: Hfootnote.1
pdftex: define anchor at line 15: page.1

Mit "longtable*":
pdftex: define anchor at line 8: section.1
pdftex: bookmark at 8: {1}{\ifnum 1>\c@secnumdepth \else \protect \numberline {
\csname thesection\endcsname }\fi Test}{section.1}{1}{toc}
pdftex: define anchor at line 13: section.1
pdftex: define anchor at line 15: page.1

### 2017-04-24 caption/issues/08-04-10a.tex
added caption package, figures and edited paper

X-Hamster-Info: Score=0 ScoreLoad=0 ScoreSave=0 Received=20080410133315
Xref: localhost de.comp.text.tex:97518
Path: newsspool2.arcor-online.net!news.arcor.de!newsspool1.arcor-online.net!newsfeed.arcor.de!news.netcologne.de!newsfeed-fusi2.netcologne.de!fu-berlin.de!newsoffice.de!not-for-mail
From: Jürgen Göbel <jg89233@yahoo.de>
Newsgroups: de.comp.text.tex
Subject: Problem bei Kombination von caption und float
Date: Thu, 10 Apr 2008 10:12:03 +0200
Organization: Newsoffice.de - http://www.newsoffice.de
Lines: 59
Sender: Jürgen Göbel <jg89233@yahoo.de>
Message-ID: <1207815123.59@user.newsoffice.de>
Mime-Version: 1.0
Content-Type: text/plain; charset=iso-8859-1; format=flowed
Content-Transfer-Encoding: 8bit
X-Trace: stgb.info 1207815123 16877 127.0.0.1 (10 Apr 2008 08:12:03 GMT)
X-Complaints-To: usenet@stgb.info
NNTP-Posting-Date: Thu, 10 Apr 2008 08:12:03 +0000 (UTC)
User-Agent: Newsoffice.de - based on NewsPortal
X-Abuse-Management: yNTJx+fG2dbUlMbF19uVzdqhVYWfpWNVYWFVpN2jQGeaYm5VaWFan6mrUGdVY2BrmqY=
X-Old-Xref: newsspool2.arcor-online.net de.comp.text.tex:221227

Moin,

beim folgenden Beispiel ergibt sich nach Aktualisieren des
caption-Paketes ein Problem. Die Bildunterschrift erscheint
nicht mehr im "Rahmen" der Beispielumgebung, sondern unterhalb
davon. Mit der älteren Version (2006) war das nicht der Fall.
Ich habe natürlich die Möglichkeit, mir die alte Version zu
reaktivieren, aber das ist ja wohl nicht der richtige Weg.

Was kann/muss ich denn da jetzt machen?

Gruß

Jürgen

\documentclass{scrbook}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{caption}
\usepackage{float}
\usepackage{graphicx}

 \floatstyle{plain}
 \newfloat{beispielfloat}{htbp}{lob}

 \newlength{\ITCVbeispiellena}
 \setlength{\ITCVbeispiellena}{\widthof{$\vartriangleright$}}
 \newenvironment{test}[3][htb]{%
    \begin{beispielfloat}[#1]
    \noindent$\vartriangleright$%
    \rule[0.535ex]{\linewidth-2\ITCVbeispiellena}{0.35pt}%
    $\vartriangleleft$%
    \par
    \noindent Beispiel 1%
 }{%
    \noindent$\vartriangleright$%
    \rule[0.535ex]{\linewidth-2\ITCVbeispiellena}{0.35pt}%
    $\vartriangleleft$%
    \end{beispielfloat}
 }

\begin{document}
 \begin{test}{}{}

  Test

  \begin{figure}[H]
  A
  \caption{Test}
  \end{figure}

  Test

 \end{test}
\end{document}

### 2017-04-24 caption/issues/08-04-10b.tex
added caption package, figures and edited paper

% http://www.mrunix.de/forums/showthread.php?t=57859

\documentclass[12pt]{scrartcl}
%\usepackage[T1]{fontenc}
\usepackage{graphicx,tabularx,ngerman,longtable,amsmath}
%\usepackage[latin1]{inputenc}
\usepackage{caption}

%\numberwithin{figure}{section}

\begin{document}
%Normale Figure
\begin{figure}\rule{2cm}{1cm}\caption{normales /caption in Figure}\end{figure}

%mit \captionof
\rule{3cm}{2cm}\\ \captionof{figure}{Der /captionof im normalen Text}

%Die longtable
\begin{longtable}{|p{0.3\textwidth}|p{0.7\textwidth}|}\hline
text Bla Bla \par text Bla Bla Bla Bla Bla Bla Bla Bla Bla Bla text  \par text Bla 
&
\begin{minipage}[t]{\linewidth}%
  \vspace{0.1mm}\centering\rule{3cm}{3cm}%
  \captionof{figure}{Der /Captionbefehl von voss}%
  \vspace{0.1mm}%
  \end{minipage}\\
\hline
\end{longtable}

\listoffigures

\end{document}

### 2017-04-24 caption/issues/08-07-28.tex
added caption package, figures and edited paper

\iffalse
Message-ID: <488DDAF4.3030707@gmail.com>
Date: Mon, 28 Jul 2008 11:43:00 -0300
From: "S.M.A. Saleem" <smasaleem@gmail.com>
User-Agent: Thunderbird 2.0.0.16 (Windows/20080708)
To: Axel Sommerfeldt <caption@sommerfee.de>
Subject: Re: subcaption package help needed
In-Reply-To: <5.2.1.1.2.20070929180735.01a57a08@post.strato.de>

Dear Axel,
I switched to subcaption package from subfig package due to the 
unsatisfactory performance of the latter with the hyperref package.  I 
am using the subfloat command provided in the subcaption package.  I 
have the following 3 questions from you.

-----------------------------------------
Question 1. When I am including a subfloat as given below, I am getting 
the warning as given below.  Therefore, I am getting 'Figure ??' inside 
my document where ever I refer to these subfloats.

\documentclass{report}
\usepackage[labelfont=bf]{caption}
\usepackage[list=true]{subcaption}
\usepackage{graphicx}
\usepackage[dvips]{hyperref}
\begin{document}
\listoffigures{}

\begin{figure}[htbp]
\subfloat[Voltage at the Local End.]{
\label{fig:case15:subfig1}
\includegraphics[width=0.45\linewidth]{%
rad_srcvolt}
}\hfill
\subfloat[FFT Local End.]{
\label{fig:case15:subfig2}
\includegraphics[width=0.45\linewidth]{%
srcvolt_fft}
}
\caption{Simulation Results.}
\label{fig:simresults}
\end{figure}

\end{document}

**************
Warnings:
1- \label before \caption ignored on line 19

2- There were undefined references
-----------------------------------------
Question 2. The list of figures is showing as,

2.1 Simulation Results.              ...5
     a Voltage at the Local End.      ...5
     b FFT Local End.                 ...5

while I want to show as,
2.1 Simulation Results.              ...5
     (a) Voltage at the Local End.    ...5
     (b) FFT Local End.               ...5
------------------------------------------
Question 3. Although, the references to subfloats are not working now as 
given in question 1,
but once they work I need the references inside the text such as,
See Figure~\ref{fig:simresults}\subref{fig:case15:subfig1}

to appear as,
See Figure 2.1(a)

and not as,
See Figure 2.1a
------------------------------------------

I would appreciate your help in this regard.

Best regards,
Syed Saleem
\fi

\documentclass{report}
\usepackage[labelfont=bf]{caption}
\usepackage[list=true,labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}
\usepackage[demo]{graphicx}
\usepackage{hyperref}
\begin{document}
\listoffigures{}

\begin{figure}[htbp]
\subfloat[Voltage at the Local End.\label{fig:case15:subfig1}]{
\includegraphics[width=0.45\linewidth]{%
rad_srcvolt}
}\hfill
\subfloat[FFT Local End.\label{fig:case15:subfig2}]{
\includegraphics[width=0.45\linewidth]{%
srcvolt_fft}
}
\caption{Simulation Results.}
\label{fig:simresults}
\end{figure}

See Figure~\ref{fig:simresults}\subref{fig:case15:subfig1}
\end{document}

### 2017-04-24 caption/issues/08-09-25.tex
added caption package, figures and edited paper

% http://www.mrunix.de/forums/showthread.php?t=61141
% Falsche Nummerierung bei "within=section" in Klassen mit \chapter

\iffalse

mrunix.de (http://www.mrunix.de/forums/index.php) 
-   LaTeX-Forum (http://www.mrunix.de/forums/forumdisplay.php?f=38) 
-   -   andere Grafiken-Nummerierung einstellen (http://www.mrunix.de/forums/showthread.php?t=61141) 
TobiD	25-09-2008 00:11

andere Grafiken-Nummerierung einstellen

Hallo!
Ich habe ein kleines Problem, welches ich durch die Forensuche und das Grafiken-FAQ-Pdf nicht lösen konnte.

Ich habe ein Dokument vom Typ scrreprt. Die eingefügten Grafiken werden einfach folgendermaßen nummeriert:
1.1
1.2
1.3
...
Ich würde es aber lieber folgendermaßen haben:

1 Kapitel1

1.1 Abschnitt1
-Grafik1-
Abbildung 1.1.1: ...
...
-Grafik2-
Abbildung 1.1.2: ...
1.2 Abschnitt2
-Grafik3-
Abbildung 1.2.1: ...

2 Kapitel2

2.1 Abschnitt1
-Grafik4-
Abbildung 2.1.1: ...
...

So dass auch im \listoffigures diese Nummerierung angezeigt wird.
Ich hoffe, dass ihr versteht, was ich meine. Ich finde es nämlich sinnlos, dass im Kapitel 3 eine Grafik die Bezeichnung "1.9" hat.
Kann mir da jemand weiterhelfen?

Stefan_K	25-09-2008 00:44

chngctr

Hallo Tobi,

willkommen im Forum!
Schau einmal hier in der UK TeX FAQ: Running equation, figure and table numbering.

Viele Grüße,

Stefan

localghost	25-09-2008 08:47

Alternative

Die aktuelle Version von caption bietet eine weitere Möglichkeit zur Gestaltung der Nummerierung.
Code:
\usepackage[font=small,labelfont=bf]{caption}
\captionsetup{%
  figurewithin=section,
  tablewithin=section
}
Ich weiß jetzt gerade nicht, ob KOMA Script das nicht auch bietet. Aber darüber sollte dessen Anleitung ja Auskunft geben.

MfG
Thorsten¹

TobiD	25-09-2008 21:27

Danke für die Antwort! Mit caption haut es hin - allerdings hat es erst mal eine vierstellige statt einer dreistelligen Nummer angezeigt; Ich habs wie folgt umdefiniert:
Code:
\captionsetup{figurewithin=section}
  \renewcommand\thefigure{\arabic{chapter}.\arabic{section}.\arabic{figure}}
  \captionsetup{tablewithin=section}
  \renewcommand\thetable{\arabic{chapter}.\arabic{section}.\arabic{table}}
So hauts hin. Problem gelöst :cool:

localghost	25-09-2008 21:41

Zeig her

Zitat:Zitat von TobiD (Beitrag 276831) 
Danke für die Antwort! Mit caption haut es hin - allerdings hat es erst mal eine vierstellige statt einer dreistelligen Nummer angezeigt […]

Zeige mir das doch bitte mal an einem Minimalbeispiel.

sommerfee	25-09-2008 21:58

Zitat:Zitat von localghost (Beitrag 276834) 
Zeige mir das doch bitte mal an einem Minimalbeispiel.

Mir auch! Denn wenn das ein Fehler im caption-Paket ist (und danach sieht es ja aus), würde ich gerne die Chance bekommen, den Fehler zu beseitigen.

Liebe Grüße,
Axel

TobiD	25-09-2008 23:03

Ok, ich werds versuchen...

Code:
\documentclass[a4paper,11pt]{scrreprt}
\usepackage[ngerman]{babel}

\usepackage{graphicx}
\usepackage{caption}
 \captionsetup{%
  figurename=Graphik,
  listfigurename=Graphikverzeichnis,
  labelfont={footnotesize,bf},
  tablewithin=section,
  figurewithin=section
  }

\begin{document}

\tableofcontents
\listoffigures

\chapter{Kapitel1}

\section{Bereich1}

\subsection{Unterbereich1}
\begin{figure}
\includegraphics{Bild1.eps}
\caption{Bild1}
\end{figure}
\subsection{Unterbereich2}
\begin{figure}
\includegraphics{Bild2.eps}
\caption{Bild2}
\end{figure}

\section{Bereich2}

\subsection{Unterbereich1}
\begin{figure}
\includegraphics{Bild3.eps}
\caption{Bild3}
\end{figure}

\end{document}

Man sieht außerdem, dass im Grafikverzeichnis ein Anzeigefehler der Nummerierung vorliegt.

rais	26-09-2008 09:47

Moin moin,
Zitat:Zitat von sommerfee (Beitrag 276836) 
Mir auch! Denn wenn das ein Fehler im caption-Paket ist (und danach sieht es ja aus), würde ich gerne die Chance bekommen, den Fehler zu beseitigen.

sieht wirklich so aus:
Code:
\listfiles
\documentclass{scrreprt}
\usepackage[figurewithin=section]{caption}
\begin{document}
%\show\thefigure
\addtocounter{chapter}{2}
\chapter{foo}
\section{bar}
\section{baz}
\begin{figure}
\caption{Test}
\end{figure}
\end{document}
mit
Code:
*File List*
scrreprt.cls    2008/01/30 v2.98b KOMA-Script document class (report)
scrkbase.sty    2008/01/30 v2.98b KOMA-Script package (basics and keyval use)
  keyval.sty    1999/03/16 v1.13 key=value parser (DPC)
scrlfile.sty    2007/12/18 v2.98 KOMA-Script package (loading files)
  size11.clo    2005/09/16 v1.4f Standard LaTeX file (size option)
typearea.sty    2008/01/30 v2.98b KOMA-Script package (type area)
 caption.sty    2008/08/24 v3.1j Customizing captions (AR)
caption3.sty    2008/08/24 v3.1j caption3 kernel (AR)
 ***********
gibt `Figure 3.3.2.1' -- hier sieht man auch, daß der Kapitelzähler doppelt ausgegeben wird. Mit aktiviertem \show\thefigure:
Code:
> \thefigure=macro:
->\ifnum \c@chapter >\z@ \thechapter .\fi \ifnum \c@section >\z@ \thesection .\
fi \arabic {figure}.
l.5 \show\thefigure
eben: \thechapter ist im \thesection schon mit drin.;)

MfG

sommerfee	27-09-2008 09:51

Ja, da habe ich wohl Mist gebaut. Das hat definitiv mal funktioniert, da muß bei den letzten zwischen-Tür-und-Angel-Änderungen am caption-Paket was schief gelaufen sein. Ich werde versuchen, nächstes Wochenende eine neue Version zu basteln, und im Winter werde ich dann hoffentlich etwas mehr Zeit für das caption-Paket finden, um die Anleitung nachzupflegen etc.

Gruß,
Axel

Alle Zeitangaben in WEZ +1. Es ist jetzt 12:32 Uhr.

Powered by vBulletin® Version 3.8.6 (Deutsch)
Copyright ©2000 - 2010, Jelsoft Enterprises Ltd.
\fi

\documentclass[a4paper,11pt]{scrreprt}
\usepackage[ngerman]{babel}

\usepackage[demo]{graphicx}
\usepackage{caption}
 \captionsetup{%
   figurename=Graphik,
   listfigurename=Graphikverzeichnis,
   labelfont={footnotesize,bf},
   tablewithin=section,
   figurewithin=section
   }

\begin{document}

\tableofcontents
\listoffigures

\chapter{Kapitel1}

\section{Bereich1}

\subsection{Unterbereich1}
\begin{figure}
\includegraphics{Bild1.eps}
\caption{Bild1}
\end{figure}
\subsection{Unterbereich2}
\begin{figure}
\includegraphics{Bild2.eps}
\caption{Bild2}
\end{figure}

\section{Bereich2}

\subsection{Unterbereich1}
\begin{figure}
\includegraphics{Bild3.eps}
\caption{Bild3}
\end{figure}

\end{document}

### 2017-04-24 caption/issues/08-10-01.tex
added caption package, figures and edited paper

\iffalse
From: Jens Saak <jens.saak@mathematik.tu-chemnitz.de>
Organization: TU Chemnitz MiIT 
To: caption@sommerfee.de
Subject: Subcation/Subfigure und Kapitel
Date: Wed, 1 Oct 2008 12:05:34 +0200
User-Agent: KMail/1.9.6 (enterprise 20070904.708012)
Message-Id: <200810011205.38818.jens.saak@mathematik.tu-chemnitz.de>

Hallo,
anbei ein kleines Minimalbeispiel, dass meines Erachtens einen Fehler des=20
subcation Paketes bei der Verwendung von kapitelbasierten Dokumentklassen=20
aufzeigt.

Offenbar wird der subcaption counter nicht zur=FCckgesetzt, wenn es nur ein=
e=20
=46igure mit subfigures/-captions in einem Kapitel gibt.  Kommentiert man=20
dagegen die Zeile \chapter{Test2} aus , so dass das erste Kapitel die beide=
n=20
ersten Abbildungen enth=E4lt, dann funktioniert das ganze (f=FCr den n=E4ch=
sten=20
Kapitelwechsel) korrekt.

Die Testumgebung:
TexLive2008=20

Das Testfile zeigt aber bei einer =E4lteren TexLive2007-Installation mit de=
n=20
gleichen (neuesten) Versionen von caption und subcaption dasselbe Verhalten.

Ansonsten finde ich aber das Paket absolut hervorragend. subfigure und subf=
ig=20
hatten mir zuvor derart viele graue Haare beim zusammenspiel mit hyperref=20
beschert, dass es ein reiner Segen ist wie problemlos hier alles=20
funktioniert, bis eben auf diese Kleinigkeit.

Danke f=FCr dieses sch=F6ne Paket,
Jens Saak

=2D-=20
=2D----------------------------------------------------------
Jens Saak
=46akult=E4t f=FCr Mathematik
TU Chemnitz
D-09107 Chemnitz
Germany

Tel.   : (+49)(0)371 531 32142
=46ax.   : (+49)(0)371 531 22509
E-mail : jens.saak@mathematik.tu-chemnitz.de
URL    : http://www-user.tu-chemnitz.de/~saak
\fi

\listfiles
\documentclass{book}

%\usepackage[pdftex]{graphicx}
\usepackage[list=true]{caption,subcaption}
%\usepackage[pdftex]{hyperref}

\begin{document}
\listoffigures

\chapter{Test}
\begin{figure}
  \begin{subfigure}[b]{.5\linewidth}
    \centering\large A
    \caption{A subfigure}\label{fig:1a}
  \end{subfigure}%
  \begin{subfigure}[b]{.5\linewidth}
    \centering\large B
    \caption{Another subfigure}\label{fig:1b}
  \end{subfigure}
  \caption{A figure}\label{fig:1}
\end{figure}

%\chapter{Test2}
\begin{figure}
  \begin{subfigure}[b]{.5\linewidth}
    \centering\large A
    \caption{A  second subfigure}\label{fig:2a}
  \end{subfigure}%
  \begin{subfigure}[b]{.5\linewidth}
    \centering\large B
    \caption{Another second subfigure}\label{fig:2b}
  \end{subfigure}
  \caption{A second figure}\label{fig:2}
\end{figure}

\chapter{Test3}
\begin{figure}
  \begin{subfigure}[b]{.5\linewidth}
    \centering\large A
    \caption{A third subfigure}\label{fig:3a}
  \end{subfigure}%
  \begin{subfigure}[b]{.5\linewidth}
    \centering\large B
    \caption{Another third subfigure}\label{fig:3b}
  \end{subfigure}
  \caption{A third figure}\label{fig:3}
\end{figure}

\chapter{Test4}
\begin{figure}
  \begin{subfigure}[b]{.5\linewidth}
    \centering\large A
    \caption{A fourth subfigure}\label{fig:4a}
  \end{subfigure}%
  \begin{subfigure}[b]{.5\linewidth}
    \centering\large B
    \caption{Another fourth subfigure}\label{fig:4b}
  \end{subfigure}
  \caption{A fourth figure}\label{fig:4}
\end{figure}
\end{document}

%%% Local Variables:
%%% mode: TEX-PDF
%%% TeX-master: t
%%% End:

### 2017-04-24 caption/issues/08-10-16.tex
added caption package, figures and edited paper

\iffalse
From: Rainer Finocchiaro <rai...@NOSPAM.demag.rwth-aachen.de.INVALID>
Newsgroups: de.comp.text.tex
Subject: =?ISO-8859-15?Q?Inkompatibilit=E4t_von_listings_und_capt?=
 =?ISO-8859-15?Q?ion=3F_=28Caption_zu_tief_gesetzt=29?=
Date: Thu, 16 Oct 2008 17:39:31 +0200
Lines: 38
Message-ID: <6lp5hjFdjsahU1@mid.dfncis.de>
User-Agent: Thunderbird 2.0.0.16 (Windows/20080708)

Hallo zusammen,

wenn ich mit dem Paket listings eine floating lstlisting-Umgebung nutze
und dazu das Paket caption lade, wird die Caption zu tief gesetzt.
Kommentiere ich das Paket caption aus, so stimmt der Abstand zwischen
Caption und Rahmen.

Minimalbeispiel:
-------------------------------------------------------------------
\fi

\documentclass{minimal}
\usepackage{listings}
\usepackage{caption}   % Für korrektes(?) Verhalten auskommentieren

\listfiles
\begin{document}
\begin{lstlisting}[float,caption=Eine Caption,frame=trbl]
Programmtext
\end{lstlisting}
\end{document}
-------------------------------------------------------------------

Ist das ein bekanntes Problem?

Grüße,
Rainer

PS: output von \listfiles
 *File List*
 minimal.cls    2001/05/25 Standard LaTeX minimal class
listings.sty    2007/02/22 1.4 (Carsten Heinz)
  keyval.sty    1999/03/16 v1.13 key=value parser (DPC)
 lstmisc.sty    2007/02/22 1.4 (Carsten Heinz)
listings.cfg    2007/02/22 1.4 listings configuration
 caption.sty    2008/08/24 v3.1j Customizing captions (AR)
caption3.sty    2008/08/24 v3.1j caption3 kernel (AR)

### 2017-04-24 caption/issues/08-12-05.tex
added caption package, figures and edited paper

% Mit pdfLaTeX übersetzen!

\iffalse
Return-Path: <oberdiek@uni-freiburg.de>
Received: from compute1.internal (compute1.internal [10.202.2.41])
	 by store65m.internal (Cyrus v2.3.13-fmsvn17160) with LMTPA;
	 Wed, 10 Dec 2008 12:18:43 -0500
X-Sieve: CMU Sieve 2.3
X-Spam-known-sender: yes
X-Spam-score: 0.0
X-Spam-hits: BAYES_50 0.001, BAYES_USED global
X-Spam-source: IP='151.189.21.113', Host='pop3.arcor.de', Country='DE', FromHeader='de',
  MailFrom='de'
X-Spam-charsets: plain='iso-8859-1'
X-Resolved-to: sommerfee@f-m.fm
X-Mail-from: oberdiek@uni-freiburg.de
Received: from imap12.internal ([10.202.2.62])
  by compute1.internal (LMTPProxy); Wed, 10 Dec 2008 12:18:43 -0500
Received: from pop3.arcor.de [151.189.21.113] by messagingengine.com
  with POP3 for sommerfee@f-m.fm; Wed, 10 Dec 2008 12:18:41 -0500
X-DeliveredInternalDate: Wed, 10 Dec 2008 17:01:19 +0100
X-LinkName: arcor.de
X-Original-To: axel.sommerfeldt@arcor.de
Received: from mail-in-12.arcor-online.net (mail-in-12.arcor-online.net [151.189.21.52])
	by mail-in-08-z2.arcor-online.net (Postfix) with ESMTP id 1C9E92130AA
	for <axel.sommerfeldt@arcor.de>; Wed, 10 Dec 2008 17:10:25 +0100 (CET)
Received: from atlas.informatik.uni-freiburg.de (atlas.informatik.uni-freiburg.de [132.230.150.3])
	by mx.arcor.de (Postfix) with ESMTP id D68254C28E
	for <axel.sommerfeldt@arcor.de>; Wed, 10 Dec 2008 17:10:24 +0100 (CET)
Received: from remote239-01.home.uni-freiburg.de ([132.230.239.1] helo=irwin.vpn.uni-freiburg.de)
	by atlas.informatik.uni-freiburg.de with esmtpsa (TLSv1:AES256-SHA:256)
	(Exim 4.68)
	(envelope-from <oberdiek@uni-freiburg.de>)
	id 1LARdm-0001lw-4a
	for axel.sommerfeldt@arcor.de; Wed, 10 Dec 2008 17:10:24 +0100
Received: by irwin.vpn.uni-freiburg.de (Postfix, from userid 500)
	id 48EEA1789C; Wed, 10 Dec 2008 17:01:19 +0100 (CET)
Date: Wed, 10 Dec 2008 17:01:19 +0100
From: Heiko Oberdiek <oberdiek@uni-freiburg.de>
To: Axel Sommerfeldt <axel.sommerfeldt@arcor.de>
Subject: \caption@setfloatcapt
Message-ID: <20081210160118.GA12851@irwin.vpn.uni-freiburg.de>
Mime-Version: 1.0
Content-Type: text/plain; charset=iso-8859-1
Content-Disposition: inline
Content-Transfer-Encoding: 8bit
X-Virus-Scanned: ClamAV 0.94.1/8743/Wed Dec 10 16:08:45 2008 on mail-in-12.arcor-online.net
X-Virus-Status: Clean
X-DCC-ARCOR-Metrics: mail-in-08-z2 1242; Body=1 Fuz1=1 Fuz2=1
X-Arcor-Antispam:  SPF_NONE
X-ArcorSpamBlocker: Spamcount: 0 Sensitivity: 13

Hallo Axel,

nächstes Problem:

| Subject: Re: pop empty color page stack 0
| Date: Fri, 05 Dec 2008 17:41:39 +0100
| From: Enrico Gregorio <gregorio@math.unipd.it>
| Newsgroups: comp.text.tex
| Message-ID: <051220081741395248%gregorio@math.unipd.it>
| 
| Enrico Gregorio <gregorio@math.unipd.it> wrote:
| 
| > Actually it comes out when also subfig is loaded:
| 
| I should have noticed that it's not subfig's fault, but that the
| problem depends on caption:
| 
| \documentclass[a4paper]{book}
| \usepackage{color}
| \usepackage{caption}
| \usepackage{float}
| \newfloat{lis}{tbp}{lol}
| \begin{document}
| \begin{lis}
| \caption{abc}
| \end{lis}
| \end{document}
| 
| Again the loading order is irrelevant.
| 
| Ciao
| Enrico

Das ist ein Bug in \caption@setfloatcapt, es verwendet ein
\setbox mit nacktem \vbox ohne die zusätzliche Gruppe
für den Color-Support.
\fi

\documentclass[a4paper]{book}
\usepackage{color}
\usepackage{caption}
\usepackage{float}
\newfloat{lis}{tbp}{lol}

\begin{document}
\makeatletter
\show\color@begingroup
\show\color@endgroup
\show\color@vbox
\show\color@endbox
\makeatother

\begin{lis}
%%%\makeatletter
%%%\long\def\caption@setfloatcapt#1{%
%%%  \let \@makecaption \caption@@make \global \setbox \@floatcapt
%%%  % \vbox alone doesn't support color
%%%  \color@vbox#1\color@endbox
%%%}
\caption{abc}
\end{lis}
\end{document}

Der Patch zeigt jetzt nur, dass mit der zusätzlichen Gruppe
die pdfTeX-Warnung verschwindet. Das schöner hinzubekommen,
überlasse ich dir.

Viele Grüße
  Heiko <oberdiek@uni-freiburg.de>

### 2017-04-24 caption/issues/08-12-06.tex
added caption package, figures and edited paper

\iffalse
Return-Path: <zhaohscas@yahoo.com.cn>
Received-Path: <zhaohscas@yahoo.com.cn>
Date: Sat, 6 Dec 2008 14:39:31 +0800
From: Hongsheng Zhao <zhaohscas@yahoo.com.cn>
Organization: Chinese Academy of Sciences
Message-ID: <1052639304.20081206143931@yahoo.com.cn>
To: caption@sommerfee.de
Subject: Using caption package with ccaption package: ! LaTeX Error: Command \captionwidth already defined.

Dear Axel Sommerfeldt,

Consider the following minimal example:

----------------------
\documentclass{book}

\usepackage{caption}
\renewcommand\arraystretch{0.95}
\captionsetup{margin={1cm,1cm}}
\usepackage{ccaption}

\begin{document}

\begin{figure}
\centering
\bicaption[tab:mytable]{short chinese caption}{long chinese caption.}
{Fig.}{English caption.}
\rule{4cm}{3cm}
\end{figure}

\end{document}
----------------------

This will give me the following errors:

---------------------
! LaTeX Error: Command \captionwidth already defined.
               Or name \end... illegal, see p.192 of the manual.

See the LaTeX manual or LaTeX Companion for explanation.
Type  H <return>  for immediate help.
 ...

l.81 ...ionwidth}[1]{\setlength{\@contcwidth}{#1}}

?
---------------------

While the following minimal example will be OK:

--------------------------------
\documentclass{book}
\usepackage{ccaption}
\usepackage{caption}
\renewcommand\arraystretch{0.95}
\captionsetup{margin={1cm,1cm}}

\begin{document}

\begin{figure}
\centering
\bicaption[tab:mytable]{short chinese caption}{long chinese caption.}
{Fig.}{English caption.}
\rule{4cm}{3cm}
\end{figure}

\end{document}
--------------------------------

Why does this happen?  Any hints on this issue will be highly
appreciated.

Regards,
-- 
Hongsheng Zhao <zhaohscas@yahoo.com.cn> 
Xinjiang Technical Institute of Physics and Chemistry
Chinese Academy of Sciences 
GnuPG DSA: 0xD108493
2008-12-6
\fi

\documentclass{book}

\usepackage{caption}
\renewcommand\arraystretch{0.95}
\captionsetup{margin={1cm,1cm}}
\usepackage{ccaption}

\begin{document}

\begin{figure}
\centering
\bicaption[tab:mytable]{short chinese caption}{long chinese caption.}
{Fig.}{English caption.}
\rule{4cm}{3cm}
\end{figure}

\end{document}

### 2017-04-24 caption/issues/08-12-08.tex
added caption package, figures and edited paper

\iffalse
Return-Path: <zhaohscas@yahoo.com.cn>
Received: from compute1.internal (compute1.internal [10.202.2.41])
	 by store65m.internal (Cyrus v2.3.13-fmsvn17160) with LMTPA;
	 Mon, 08 Dec 2008 10:15:19 -0500
X-Sieve: CMU Sieve 2.3
X-Spam-score: 0.0
X-Spam-hits: BAYES_50 0.001, UNPARSEABLE_RELAY 0.001, BAYES_USED global
X-Spam-source: IP='81.169.145.136', Host='post.strato.de', Country='DE', FromHeader='cn',
  MailFrom='cn'
X-Spam-charsets: plain='us-ascii'
X-Resolved-to: sommerfee@f-m.fm
X-Mail-from: zhaohscas@yahoo.com.cn
Received: from imap12.internal ([10.202.2.62])
  by compute1.internal (LMTPProxy); Mon, 08 Dec 2008 10:15:19 -0500
Received: from post.strato.de [81.169.145.136] by messagingengine.com
  with POP3 for sommerfee@f-m.fm; Mon, 08 Dec 2008 10:15:18 -0500
X-DeliveredInternalDate: Mon, 8 Dec 2008 22:07:48 +0800
X-LinkName: sommerfee.de
X-Envelope-From: <zhaohscas@yahoo.com.cn>
X-Envelope-To: <ml@axel-sommerfeldt.de>
X-Delivery-Time: 1228745274
X-UID: 8429
X-RZG-FWD-BY: caption@sommerfee.de
Received: from localhost (client mail forwarder)
	by mailin.webmailer.de (zeb mi58) (RZmta 18.0)
	for <ml@axel-sommerfeldt.de>; Mon, 8 Dec 2008 15:07:54 +0100 (MET)
X-RZG-CLASS-ID: mi
Received: from yahoo.com.cn. ([159.226.135.215])
	by mailin.webmailer.de (zeb mi58) (RZmta 18.0)
	with SMTP id 606b5akB8E5G3v for <caption@sommerfee.de>;
	Mon, 8 Dec 2008 15:07:53 +0100 (MET)
Received-Path: <zhaohscas@yahoo.com.cn>
Received: from localhost[127.0.0.1] (helo=127.0.0.1) by localhost[127.0.0.1]
 with esmtp (QK SMTP Server 3);Mon, 8 Dec 2008 22:07:48 +0800
Date: Mon, 8 Dec 2008 22:07:48 +0800
From: Hongsheng Zhao <zhaohscas@yahoo.com.cn>
Organization: Chinese Academy of Sciences
X-Priority: 3 (Normal)
Message-ID: <1905206967.20081208220748@yahoo.com.cn>
To: caption@sommerfee.de
Subject: backref doesn't work with threeparttable and caption package.
MIME-Version: 1.0
Content-Type: text/plain; charset=us-ascii
Content-Transfer-Encoding: 7bit

Dear Axel,

Consider the following example:

-----------------------------
\documentclass{book}
\usepackage{caption}
\usepackage{threeparttable}
\usepackage[backref=page]{hyperref}

\begin{document}
\begin{table}[htbp]
\centering
\caption{foo}
\begin{threeparttable}
\begin{tabular}{l}
\hline
Approach $^a$\\
\hline
\end{tabular}
\begin{tablenotes}
\footnotesize
\item[a] Ref. \cite{foo}.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{thebibliography}{1}
\bibitem{foo}
foo

\end{thebibliography}

\end{document}
-----------------------------

The above example will give me the following errors:

------------------------------------
(backref_threeparttable.brf
! Argument of \@gobbletwo has an extra }.
<inserted text>
                \par
l.1 ... {??}{ on input line 18}}{table.caption.2}}

?
------------------------------------

But when I comment the following line out, it will works fine:

%\usepackage[backref=page]{hyperref}

Why does this happen, any hints will be highly appreciated.

Regards,
-- 
Hongsheng Zhao <zhaohscas@yahoo.com.cn> 
Xinjiang Technical Institute of Physics and Chemistry
Chinese Academy of Sciences 
GnuPG DSA: 0xD108493
2008-12-8
\fi

\documentclass{book}
\usepackage{caption}
\usepackage{threeparttable}
\usepackage[backref=page]{hyperref}

%\usepackage{makerobust}
%\makeatletter
%\MakeRobustCommand\caption@xref
%\makeatother

\begin{document}
\begin{table}[htbp]
\centering
\caption{foo}
\begin{threeparttable}
\begin{tabular}{l}
\hline

Approach $^a$\\
\hline
\end{tabular}
\begin{tablenotes}
\footnotesize
\item[a] Ref. \cite{foo}.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{thebibliography}{1}
\bibitem{foo}
foo

\end{thebibliography}

\end{document}

### 2017-04-24 caption/issues/09-02-25.tex
added caption package, figures and edited paper

\iffalse
From: Heiner Buesing <h_bues...@yahoo.de>
Newsgroups: de.comp.text.tex
Subject: hyperref mit pagebackref=true und subfig
Date: Wed, 25 Feb 2009 15:36:08 -0800 (PST)
Message-ID: <aeb586cc-f93b-4fb8-a528-2130495f0f7c@d19g2000yqb.googlegroups.com>

Hallo,

ich bin über ein (weiteres) Problem in Zusammenhang mit subfig
gestolpert. Es tritt auf, wenn hyperref mit der Option
pagebackref=true verwendet wird und in einer float-Umgebung ein \cite
noch vor dem \caption kommt. Ein Minimalbeispiel verdeutlicht dies:

===
\fi
\documentclass{article}
\usepackage[pagebackref=true]{hyperref}
\usepackage{subfig}
%\usepackage{makerobust}
%\makeatletter
%\MakeRobustCommand\caption@xref
%\makeatother
\begin{document}
\begin{figure}
	\centering Eine Mini-Figure \cite{blupp}.
	\caption{Referenz}
\end{figure}
\begin{thebibliography}{1}
	\bibitem[1]{blupp}
		Blupp. \newblock Titel. 2009

\end{thebibliography}
\end{document}
===

Der erste LaTeX-Aufruf läuft problemlos, in die brf-Datei wird jedoch
geschrieben:

\backcite {blupp}{{1}{\caption@xref {??}{ on input line 7}}
{figure.caption.1}}

Beim zweiten LaTeX-Aufruf kommt dann entsprechend der Fehler:

! Argument of \@gobbletwo has an extra }.
<inserted text>
                \par
l.1 ... {??}{ on input line 7}}{figure.caption.1}}

Auskommentieren von subfig behebt das Problem. Meine TeXLive 2008
Installation ist auf dem neuesten Stand:

 *File List*
 article.cls    2005/09/16 v1.4f Standard LaTeX document class
  size10.clo    2005/09/16 v1.4f Standard LaTeX file (size option)
hyperref.sty    2009/02/02 v6.78o Hypertext links for LaTeX
  keyval.sty    1999/03/16 v1.13 key=3Dvalue parser (DPC)
   ifpdf.sty    2007/12/12 v1.6 Provides the ifpdf switch (HO)
  ifvtex.sty    2008/11/04 v1.4 Switches for detecting VTeX and its
modes (HO)
 ifxetex.sty    2009/01/23 v0.5 Provides ifxetex conditional
 hycolor.sty    2008/09/08 v1.4 Code for color options of hyperref/
bookmark (HO
)
xcolor-patch.sty    2008/09/08 xcolor patch
  pd1enc.def    2009/02/02 v6.78o Hyperref: PDFDocEncoding definition
(HO)
etexcmds.sty    2007/12/12 v1.2 Prefix for e-TeX command names (HO)
infwarerr.sty    2007/09/09 v1.2 Providing info/warning/message (HO)
hyperref.cfg    2002/06/06 v1.2 hyperref configuration of TeXLive
kvoptions.sty    2007/10/18 v3.0 Keyval support for LaTeX options (HO)
 backref.sty    2006/09/05 v1.28 Bibliographical back referencing
     url.sty    2006/04/12  ver 3.3  Verb mode for urls, etc.
  bitset.sty    2007/09/28 v1.0 Data type bit set (HO)
 intcalc.sty    2007/09/27 v1.1 Expandable integer calculations (HO)
bigintcalc.sty    2007/11/11 v1.1 Expandable big integer calculations
(HO)
pdftexcmds.sty    2007/12/12 v0.3 LuaTeX support for pdfTeX utility
functions (
HO)
kvsetkeys.sty    2007/09/29 v1.3 Key value parser with default handler
support
(HO)
atbegshi.sty    2008/07/31 v1.9 At begin shipout hook (HO)
 hpdftex.def    2009/02/02 v6.78o Hyperref driver for pdfTeX
  subfig.sty    2005/06/28 ver: 1.3 subfig package
 caption.sty    2008/08/24 v3.1j Customizing captions (AR)
caption3.sty    2008/08/24 v3.1j caption3 kernel (AR)
 nameref.sty    2007/05/29 v2.31 Cross-referencing by name of section
refcount.sty    2008/08/11 v3.1 Data extraction from references (HO)
Beispiel.out
Beispiel.out
 ***********

Hat jemand eine Idee zur Abhilfe, wenn auf Unter-Abbildungen nicht
verzichtet werden kann?

Dank und Gruß
Heiner

### 2017-04-24 caption/issues/09-05-18.tex
added caption package, figures and edited paper

% http://www.golatex.de/fehler-bei-kombination-von-usepackagecaption-und-bac-t2698.html
\errorcontextlines=5

\iffalse
Hallo allerseits,

ganz kurz zu mir: 
ich heiße Steffen, fang demnächst mit meiner Bachelorarbeit an und das ist mein erster Beitrag hier.

Mein Problem: 
Mich hat gestört, dass die Bildunterschrift caption immer mittig ist. Deswegen hab ich \usepackage{caption} eingebunden. Zu meiner Überraschung hab ich dann aber die für mich nicht verständliche Fehlermeldung "Undefined control sequence" erhalten.

Nach einigem Hin und Her hab ich dann ein Minimalbeispiel vorbereitet, um es hier einzustellen und beim Runterkürzen des Codes fiel mit auf, dass dieser Fehler nur in Verbindung mit \usepackage{bar} auftritt, was ich noch viel weniger einordnen kann.

Mir geht es jetzt nur darum, irgendwie zu verstehen, wie da die Zusammenhänge sind und sicher zu stellen, dass da nicht irgendein ganz anderer Fehler dahintersteckt, den ich noch gar nicht entdeckt hab.

Zum Nachprüfen: 
Wenn ich den Code so durchlaufen lasse, springt TeXnic Center in die Zeile mit 
\caption{Das ist der Text der Bildunterschrift} und gibt zwei Fehlermeldungen aus:

Undefined control sequence 
<argument> \setspace@singlespace

Missing number, treated as zero 
<to be read again>

Kommentiere ich die Zeile 
\usepackage{bar} 
(und den zugehörigen Absatz beginnend mit \begin{barenv}) aus, läuft das Beispiel ohne Fehlermeldung durch.

Grüße Steffen
\fi

\documentclass[
   a4paper,
   12pt,
   ]{scrreprt}

% eingebundene Pakete: --------------
   \usepackage[english,ngerman]{babel}
   \usepackage[demo]{graphicx}          % Grafikintegration
   \usepackage{bar}            % Diagramme
   \usepackage[               % Bilderunterschriften
   format=plain,
   labelformat=default,
   justification=raggedright,
   singlelinecheck=false,
   ]{caption}

% Beginn Body: ----------------
\begin{document}

\chapter{Probleme mit Bildunterschriften}

   \begin{figure}[htbp]            % Bild mit Bildunterschrift
      \centering
         \includegraphics{bilder/bildname}
              \caption{Das ist der Text der Bildunterschrift}
              \label{fig:bildname}
   \end{figure}

   \begin{barenv}                     % Schaubild
   \setxaxis{1}{4}{1} \setxname{Quartal}
   \setyaxis[0]{0}{50}{10} \setyname{Anzahl}
   \bar{10}{6}% \bar{Höhe}{Schraffur}[Beschreibung]
   \bar{30}{6}
   \bar{25}{6}
   \end{barenv}

\end{document}

### 2017-04-24 caption/issues/09-08-12b.tex
added caption package, figures and edited paper

% http://www.golatex.de/cite-in-subfig-t2953.html

\iffalse
Ich habe jetzt eine Grafik ins Subcaption-Paket umgesetzt. Es funktioniert auch soweit so, wie ich mir das vorgestellt hatte. 
Allerdings musste ich das floatrow-Package auskommentieren, da es sich mit dem Subcaption-Package nicht vertragen hat (Fehlermeldung: Caption(s) lost.). Das brauche ich dann auch nicht unbedingt, aber ich hatte vorher mit Hilfe des Befehls Code:

\floatsetup[figure]{style=BOXED}

einen Rahmen um jede Figure. Den hätte ich gerne wieder. 
Mit \fbox bekomme ich aber nur einen Rahmen, der die Caption ausschließt. Was ist da die einfachste Möglichkeit bzw. was mache ich falsch? Am schönsten wäre es natürlich, wenn man global einen Rahmen um alle figures definieren könnte, damit ich das nicht jedes Mal da stehen habe.
\fi

\documentclass[11pt,listof=totoc,bibliography=totoc,version=first]{scrbook}

\usepackage[demo]{graphicx} %Grafikpaket

%-----------------------------
\usepackage{floatrow} %Definitionen für Gleitobjekte (z.B. Rahmen)
\floatsetup[figure]{style=BOXED} %Rahmen um figure Gleitobjekte und Captions

\usepackage{caption} %Bildunterschriften
\usepackage{subcaption}
%--------------------------------------------------------------------------------------------------------------------------

\begin{document}

\chapter{Kapitel}
\label{sec:Kapitel}

\section{Abschnitt}
\label{sec:Abschnitt}

\begin{figure}[htbp]
	\centering
	\begin{subfigure}[t]{.4\linewidth}
		\centering
		\includegraphics[height=4cm]{a.jpg}\newline
		%\cite{bild:EPC-Label}
		\caption{Komponente A.}
		\label{fig:KomponenteA}
	\end{subfigure}%
	\hspace{1cm}
	\begin{subfigure}[t]{.4\linewidth}
		\centering
		\includegraphics[height=4cm]{b.jpg}\newline
		%\cite{bild:EPC-Durchgangsleser}
		\caption{Komponente B.}
		\label{fig:KomponenteB}		
	\end{subfigure}
	\caption{Komponenten}
\end{figure}

\begin{figure}
	\begin{subfigure}[b]{.5\linewidth}
		\centering\large A
		\newline\caption{A subfigure}\label{fig:1a}
	\end{subfigure}%
	\begin{subfigure}[b]{.5\linewidth}
		\centering\large B
		\newline\caption{Another subfigure}\label{fig:1b}
	\end{subfigure}
	\caption{A figure}\label{fig:1}
\end{figure}

\end{document}

### 2017-04-24 caption/issues/09-09-29.tex
added caption package, figures and edited paper

\iffalse
Return-Path: <Herbert.Voss@FU-Berlin.DE>
Received: from compute1.internal (compute1.internal [10.202.2.41])
	 by store65m.internal (Cyrus v2.3.15-fmsvn20544-ebff1b04) with LMTPA;
	 Tue, 29 Sep 2009 17:13:36 -0400
X-Sieve: CMU Sieve 2.3
X-Spam-score: 0.0
X-Spam-hits: BAYES_00 -2.599, BAYES_USED global
X-Spam-source: IP='151.189.21.113', Host='pop3.arcor.de', Country='DE', FromHeader='DE',
  MailFrom='DE'
X-Spam-charsets: plain='ISO-8859-1'
X-Resolved-to: sommerfee@f-m.fm
X-Mail-from: Herbert.Voss@FU-Berlin.DE
Received: from imap12.internal ([10.202.2.62])
  by compute1.internal (LMTPProxy); Tue, 29 Sep 2009 17:13:49 -0400
Received: from pop3.arcor.de [151.189.21.113] by messagingengine.com
  with POP3 for sommerfee@f-m.fm; Tue, 29 Sep 2009 17:13:35 -0400
X-DeliveredInternalDate: Tue, 29 Sep 2009 22:34:20 +0200
X-LinkName: arcor.de
X-Original-To: axel.sommerfeldt@arcor.de
Received: from mail-in-06.arcor-online.net (mail-in-06.arcor-online.net [151.189.21.46])
	by mail-in-06-z2.arcor-online.net (Postfix) with ESMTP id 1C0E05BE3C
	for <axel.sommerfeldt@arcor.de>; Tue, 29 Sep 2009 22:34:22 +0200 (CEST)
Received: from outpost1.zedat.fu-berlin.de (outpost1.zedat.fu-berlin.de [130.133.4.66])
	by mx.arcor.de (Postfix) with ESMTP id E476639A838
	for <axel.sommerfeldt@arcor.de>; Tue, 29 Sep 2009 22:34:21 +0200 (CEST)
X-DKIM: Sendmail DKIM Filter v2.8.2 mx.arcor.de E476639A838
Received: from inpost2.zedat.fu-berlin.de ([130.133.4.69])
          by outpost1.zedat.fu-berlin.de (Exim 4.69)
          for axel.sommerfeldt@arcor.de with esmtp
          (envelope-from <Herbert.Voss@FU-Berlin.DE>)
          id <1MsjOv-0006Ht-EF>; Tue, 29 Sep 2009 22:34:21 +0200
Received: from p54bfcde1.dip.t-dialin.net ([84.191.205.225] helo=[192.168.1.12])
          by inpost2.zedat.fu-berlin.de (Exim 4.69)
          for axel.sommerfeldt@arcor.de with esmtpsa
          (envelope-from <Herbert.Voss@FU-Berlin.DE>)
          id <1MsjOv-0003Hp-8G>; Tue, 29 Sep 2009 22:34:21 +0200
Message-ID: <4AC26F4C.8080801@FU-Berlin.DE>
Date: Tue, 29 Sep 2009 22:34:20 +0200
From: Herbert Voss <Herbert.Voss@FU-Berlin.DE>
Organization: Freie =?ISO-8859-1?Q?Universit=E4t_Berlin?=
User-Agent: Thunderbird 2.0.0.23 (X11/20090817)
MIME-Version: 1.0
To: Axel Sommerfeldt <axel.sommerfeldt@arcor.de>
Subject: Re: caption und Format
References: <4AA4007C.7020909@FU-Berlin.DE> <1252352341.4329.1333630667@webmail.messagingengine.com> <4ABF2059.7010404@FU-Berlin.DE> <1254160234.14485.1337016555@webmail.messagingengine.com>
In-Reply-To: <1254160234.14485.1337016555@webmail.messagingengine.com>
Content-Type: text/plain; charset=ISO-8859-1
Content-Transfer-Encoding: 8bit
X-Originating-IP: 84.191.205.225
X-DCC-ARCOR-Metrics: mail-in-06-z2 1242; Body=1 Fuz1=1 Fuz2=1
X-Arcor-Antispam:  SPF_PASS IN_REPLY_TO
X-ArcorSpamBlocker: Spamcount: -4 Sensitivity: 13

> Ich habe leider noch ein paar andere Fehler in der Pipeline, aber ich
> habe mir f¸r Ende Oktober 3 Tage Urlaub genommen, um endlich mal die
> restlichen bekannten Fehler zu beheben und eine neue Version des
> caption-Paketes fertigzubekommen, denn mit hˆchstens hier-und-da mal
> eine Stunde am Abend bin ich (wie man sieht) bisher nicht sehr weit
> gekommen.

Hallo Axel,

Ja, da genieﬂe ich den Luxus des Vorruhestands ... :-)
Deshalb hier wieder ein Problem, was wohl auf Olgas Kappe geht
oder meine :-) Leider antwortet Olga nicht. Wenn es definitiv
nichts mit caption zu hat, dann vergiss es ...

Er kennt relatedcapstyle nicht ...
\fi

\documentclass{article}

\usepackage{caption,floatrow}
\DeclareCaptionStyle{Beispiel}{font=small}
\DeclareNewFloatType{Beispiel}{relatedcapstyle=yes}

\begin{document}
foo
\end{document}

! LaTeX Error: Missing \begin{document}.

See the LaTeX manual or LaTeX Companion for explanation.
Type  H <return>  for immediate help.
 ...

l.5 ...NewFloatType{Beispiel}{relatedcapstyle=yes}

! Bad space factor (0).
<recently read> \@savsf

l.5 ...NewFloatType{Beispiel}{relatedcapstyle=yes}

Herbert

### 2017-04-24 caption/issues/09-11-14.tex
added caption package, figures and edited paper

\iffalse
Return-Path: <raphael.attie@mac.com>
Received: from compute1.internal (compute1.internal [10.202.2.41])
	 by store65m.internal (Cyrus v2.3.15-fmsvn20544-ebff1b04) with LMTPA;
	 Sat, 14 Nov 2009 11:01:05 -0500
X-Sieve: CMU Sieve 2.3
X-Spam-score: 0.0
X-Spam-hits: BAYES_00 -2.599, UNPARSEABLE_RELAY 0.001, BAYES_USED global
X-Spam-source: IP='81.169.145.136', Host='post.strato.de', Country='DE', FromHeader='com',
  MailFrom='com'
X-Spam-charsets: plain='US-ASCII', html='US-ASCII'
X-Resolved-to: sommerfee@f-m.fm
X-Mail-from: raphael.attie@mac.com
Received: from imap12.internal ([10.202.2.62])
  by compute1.internal (LMTPProxy); Sat, 14 Nov 2009 11:01:05 -0500
Received: from post.strato.de [81.169.145.136] by messagingengine.com
  with POP3 for sommerfee@f-m.fm; Sat, 14 Nov 2009 11:00:55 -0500
X-DeliveredInternalDate: Sat, 14 Nov 2009 15:19:48 +0100
X-LinkName: sommerfee.de
X-Envelope-From: <raphael.attie@mac.com>
X-Envelope-To: <ml@axel-sommerfeldt.de>
X-Delivery-Time: 1258208395
X-UID: 8863
X-RZG-FWD-BY: caption@sommerfee.de
Received: from RZmta-intern (client mail forwarder)
	by mailin.webmailer.de (blert mi9) (RZmta 22.1)
	for <ml@axel-sommerfeldt.de>; Sat, 14 Nov 2009 15:19:55 +0100 (MET)
X-RZG-CLASS-ID: mi
Received: from asmtpout012.mac.com ([17.148.16.87])
	by mailin.webmailer.de (blert mi9) (RZmta 22.1)
	with ESMTP id i040b4lAEEFtgF for <caption@sommerfee.de>;
	Sat, 14 Nov 2009 15:19:55 +0100 (MET)
MIME-version: 1.0
Content-type: multipart/alternative;
 boundary="Boundary_(ID_8vaiOHVH+3CE5q6BOg9/XQ)"
Received: from [192.168.2.101] ([82.82.127.216])
 by asmtp012.mac.com (Sun Java(tm) System Messaging Server 6.3-8.01 (built Dec
 16 2008; 32bit)) with ESMTPSA id <0KT300NZBRT01350@asmtp012.mac.com> for
 caption@sommerfee.de; Sat, 14 Nov 2009 06:19:53 -0800 (PST)
Message-id: <C6C43F24-B476-4F35-8A4C-011256DCBFEE@mac.com>
From: Raphael Attie <raphael.attie@mac.com>
To: caption@sommerfee.de
Subject: incompatibility of caption and university book-based document class,
 no-warning-issued
Date: Sat, 14 Nov 2009 15:19:48 +0100
X-Mailer: Apple Mail (2.936)

--Boundary_(ID_8vaiOHVH+3CE5q6BOg9/XQ)
Content-type: text/plain; charset=US-ASCII; format=flowed; delsp=yes
Content-transfer-encoding: 7BIT

Dear Axel Sommerfeldt,

I have read the documentation of the caption package, as I encountered  
a problem after the update from Mactex 2007 to Mactex 2009, thus using  
the version of the \caption package.

I am using a home-made "book"-based documentclass to write my Ph.D  
thesis, provided by the Max Planck Institute for Solar System Research  
in Germany. The class files are available there :
http://www.solar-system-school.de/thesis/thesis.zip

If needed, at the end of this email I've copied-pasted the content of  
thesis.cls that I'm using (together with the copy of my document), so  
that you don't have to download the zip file.

With the older version, Mactex 2007, this exact bit is working fine.  
Since the update, the caption package no longer works, only the  
\caption2 package does. However, it doesn't offer some of the  
improvements that the current \caption offers, and which I need, thus  
I would like to make the later work. For instance, with \caption2, I  
would not know how to put the whole caption in italic, and not just  
the "figure #:", whereas it is possible with the current version of  
the caption package.

The bug report I have is not the expected warning ( thus I thought I  
should report it) that you describe in your documentation :

Package caption Warning: Unsupported document class (or package)  
detected,
(caption) usage of the caption package is not recommended.
See the caption package documentation for explanation.

Instead, I have the following :

! Undefined control sequence.
\captionlabelfont@default ->\cph@font

As it worked before with 2007 version, and also work now with  
\caption2, I understand it comes from the thesis.cls not being  
compatible anymore.

Would you know a solution ?

Thank you for your help,

Raphael Attie
Ph.D Student
Max Planck Institute for Solar System Research
Max Planck Str. 2
37191 Katlenburg-Lindau
Germany

Here is a shortened version of my document.

------------------------
\fi

\documentclass[braunschweig]{09-11-14-thesis}

\usepackage{caption}
\usepackage[tight]{subfigure}
\usepackage{epstopdf}
\usepackage{fixltx2e}
\usepackage{float}
\usepackage{amsmath}
\usepackage{txfonts}

\begin{document}

\section{Tracking the photospheric flows}

blablabla

\begin{figure*}[h]
\centering
\includegraphics[width=1 \textwidth]{./figures/photosphere1.jpeg}
\caption{Image of the solar photosphere in continuum with MDI/SoHO,  
with a close-up taken at higher resolution by FG-SOT/Hinode. The  
latter shows the granulation.}  \label{granulation}
\end{figure*}

\end{document}
------------------------

-----------------------------

%% File: thesis.cls
%%
%% Author:
%% Dieter Schmitt
%% Max Planck Institute for Solar System Research
%% Max-Planck-Str. 2
%% D-37191 Katlenburg-Lindau
%% Germany
%%
%% Email: schmitt@mps.mpg.de
%%
%% For producing a PhD thesis for digital print and online publishing
%%
\NeedsTeXFormat{LaTeX2e}[1994/06/01]
\def\MyProvidesClass#1 [#2 #3 #4]
   {\ProvidesClass{#1}[#2 #3 #4]%
    \def\clsname{#1}\def\clsdate{#2}\def\clsversion{#3}\def\clsinfo{#4}}
\MyProvidesClass{thesis} [2008/07/22 1.8 (DS)]
%%
%% Version 1.2 (12 Jul 2005): change of Braunschweig title page, vec-- 
 >vect, ...
%% Version 1.3 (01 Oct 2006): change of Braunschweig title page,  
txfonts, pdfoutput
%% Version 1.4 (22 Dec 2006): options nottoc,notlof,notlot added to  
tocbibind
%% Version 1.5 (17 Apr 2007): change of Braunschweig title page
%% Version 1.6 (12 Oct 2007): Copernicus Publications and copyright
%% Version 1.7 (05 Mar 2008): change of copyright
%% Version 1.8 (22 Jul 2008): change of description
%%
\newif\if@goe
\newif\if@bs
\newif\if@goeorbs
\newif\if@sub
\newif\if@acc
\newif\if@print
\newif\if@file
\newif\if@fem
\newif\if@german
\newif\if@hyper
\DeclareOption{goettingen}{\@goetrue\@goeorbstrue\@subtrue}
\DeclareOption{braunschweig}{\@bstrue\@goeorbstrue\@subtrue}
\DeclareOption{submitted}{\@subtrue}
\DeclareOption{accepted}{\@acctrue\@subfalse}
\DeclareOption{print}{\@printtrue\@subfalse}
\DeclareOption{file}{\@filetrue\@subfalse}
\DeclareOption{female}{\@femtrue}
\DeclareOption{german}{\@germantrue}
\DeclareOption{hyper}{\@hypertrue}
\DeclareOption*{\PassOptionsToClass{\CurrentOption}{book}}
\ProcessOptions
\LoadClass[12pt]{book}
%%
\ifx\pdfoutput\undefined\else
    \setlength{\pdfpageheight}{29.7cm}
    \setlength{\pdfpagewidth}{21.0cm}
\fi
\setlength{\paperheight}{29.7cm}
\setlength{\paperwidth}{21.0cm}
\setlength{\textheight}{23.5cm}
\setlength{\textwidth}{15.0cm}
\setlength{\headheight}{2.0cm}
\setlength{\headsep}{0.8cm}
\setlength{\topskip}{12pt}
\setlength{\footskip}{30pt}
\setlength{\oddsidemargin}{0.46cm}
\setlength{\evensidemargin}{0.46cm}
\setlength{\topmargin}{-2.0cm}
%%
\ifx\pdfoutput\undefined
    \IfFileExists{graphicx.sty}{\RequirePackage[dvips]{graphicx}% LaTeX
    \DeclareGraphicsExtensions{.eps,.ps}}{}
    \IfFileExists{color.sty}{\RequirePackage{color}}{}
\else%
    \ifnum\pdfoutput=0
       \IfFileExists{graphicx.sty}{\RequirePackage[dvips]{graphicx}%  
LaTeX
       \DeclareGraphicsExtensions{.eps,.ps}}{}
       \IfFileExists{color.sty}{\RequirePackage{color}}{}
    \else
       \IfFileExists{graphicx.sty}{\RequirePackage[pdftex]{graphicx}%  
pdfLaTeX
       \DeclareGraphicsExtensions{.pdf,.png,.jpg}}{}
       \IfFileExists{color.sty}{\RequirePackage[pdftex]{color}}{}
       \pdfinfo{/Creator (thesis.cls version \clsversion)}
    \fi
\fi
%%
%\IfFileExists{txfonts.sty}{\RequirePackage{txfonts}}{}
\IfFileExists{natbib.sty}{\RequirePackage{natbib}}{}
\bibpunct{(}{)}{,}{a}{}{,}
%\setlength{\bibsep}{0pt}
\IfFileExists{fancyhdr.sty}{\RequirePackage{fancyhdr}}{}
\IfFileExists{tocbibind.sty}{\RequirePackage[nottoc,notlof,notlot] 
{tocbibind}}{}
\IfFileExists{fontenc.sty}{\RequirePackage[T1]{fontenc}}{}
\IfFileExists{url.sty}{\RequirePackage{url}}{}
\IfFileExists{amssymb.sty}{\RequirePackage{amssymb}}{}
%\IfFileExists{amsmath.sty}{\RequirePackage{amsmath}}{}
\IfFileExists{ifthen.sty}{\RequirePackage{ifthen}}{}
\IfFileExists{array.sty}{\RequirePackage{array}}{}
\IfFileExists{multicol.sty}{\RequirePackage{multicol}}{}
%%
\if@german
    \IfFileExists{german.sty}{\RequirePackage{german}}{}
    \def\captionsgerman{%
       \def\acknowname{Danksagung}%
       \def\refname{Literaturverzeichnis}%
       \def\abstractname{Zusammenfassung}%
%     \def\appendixname{Anhang}%
       \def\figurename{Abbildung}%
       \def\tablename{Tabelle}}
    \selectlanguage{german}
\else
    \def\captionsenglish{%
       \def\acknowname{Acknowledgement}%
       \def\refname{References}%
       \def\abstractname{Abstract}%
%     \def\appendixname{Appendix}%
       \def\figurename{Figure}%
       \def\tablename{Table}}
\fi
%%
\if@hyper\IfFileExists{hyperref.sty}{\RequirePackage{hyperref}}{}\fi
%%
\DeclareRobustCommand*{\vect}[1]{\ensuremath{%
\mathchoice{\mbox{\boldmath$\displaystyle#1$}}
            {\mbox{\boldmath$\textstyle#1$}}
            {\mbox{\boldmath$\scriptstyle#1$}}
            {\mbox{\boldmath$\scriptscriptstyle#1$}}}}
%%
\DeclareRobustCommand*{\chem}[1]{\ensuremath{\mathrm{#1}}}
\DeclareRobustCommand*{\unit}[1]{\def~{\,}\ensuremath{\mathrm{#1}}}
%%
\setcounter{topnumber}{2}
\def\topfraction{1.}
\setcounter{bottomnumber}{1}
\def\bottomfraction{1.}
\setcounter{totalnumber}{3}
\def\textfraction{0.}
\def\floatpagefraction{.7}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
%%
%\sloppy\clubpenalty4000\widowpenalty4000
%%
\def\town#1{\def\@town{#1}}               \def\@town{???}
\def\refereea#1{\def\@refa{#1}}           \def\@refa{???}
\def\refereeb#1{\def\@refb{#1}}           \def\@refb{???}
\def\submitteddate#1{\def\@subdate{#1}}   \def\@subdate{???}
\def\submittedyear#1{\def\@subyear{#1}}   \def\@subyear{\number\year}
\def\examinationdate#1{\def\@exdate{#1}}  \def\@exdate{???}
\def\publicationyear#1{\def\@pubyear{#1}} \def\@pubyear{\number\year}
\def\isbn#1{\def\@isbn{#1}}               \def\@isbn{???}
%%
\def\maketitle{%
\begin{titlepage}
\if@goe
    \vspace*{20mm}
    \begin{center}
    {\Huge\bfseries\@title\par}
    \vspace{30mm}
    {\large Dissertation\\[1mm]
    zur Erlangung des Doktorgrades\\[1mm]
    der Mathematisch-Naturwissenschaftlichen Fakult\"aten\\[1mm]
    der Georg-August-Universit\"at zu G\"ottingen
    \vfill
    vorgelegt von\\[1mm]
    {\Large\bfseries\@author}\\[1mm]
    aus \@town
    \par\vspace{30mm}
    G\"ottingen \space\@subyear}
    \end{center}
\fi
\if@bs
    \if@sub
       \vspace*{10mm}
       \begin{center}
       {\Huge\bfseries\@title\par}
       \vspace{20mm}
       {\large Der Fakult\"at f\"ur Elektrotechnik,  
Informationstechnik, Physik\\[1mm]
       der Technischen Universit\"at Carolo-Wilhelmina\\[1mm]
       zu Braunschweig\\[1mm]
       zur Erlangung des Grades \if@fem einer \else eines \fi \\[1mm]
       \if@fem Doktorin \else Doktors \fi der Naturwissenschaften\\[1mm]
       (Dr.rer.nat.)\\[1mm]
       eingereichte\\[1mm]
       Dissertation
       \par\vspace{30mm}
       von \@author\\[1mm]
       aus \@town\par}
       \end{center}
       \vfill
       {\large 1. Referentin oder Referent: \@refa\\[1mm]
       2. Referentin oder Referent: \@refb\\[1mm]
       eingereicht am: \@subdate\\[1mm]
       m\"undliche Pr\"ufung (Disputation) am:\par}
    \else
       \vspace*{20mm}
       \begin{center}
       {\Huge\bfseries\@title\par}
       \vspace{30mm}
       {\large Von der Fakult\"at f\"ur Elektrotechnik,  
Informationstechnik, Physik\\[1mm]
       der Technischen Universit\"at Carolo-Wilhelmina\\[1mm]
       zu Braunschweig\\[1mm]
       zur Erlangung des Grades \if@fem einer \else eines \fi \\[1mm]
       \if@fem Doktorin \else Doktors \fi der Naturwissenschaften\\[1mm]
       (Dr.rer.nat.)\\[1mm]
       genehmigte\\[1mm]
       Dissertation
       \par\vspace{30mm}
       von \@author\\[1mm]
       aus \@town\par}
       \end{center}
    \fi
\fi
\if@goeorbs\else\IfFileExists{firstpage.tex}{\include{firstpage}}
    {Please provide file firstpage.tex}\fi
\end{titlepage}
\newpage % second page
\thispagestyle{empty}
\if@goe
    \if@sub
       \vspace*{150mm}
       \noindent {\large D7\\[1mm]
       Referent: \@refa\\[1mm]
       Korreferent: \@refb\\[1mm]
       Tag der m\"undlichen Pr\"ufung: \par}
    \fi
    \if@print
       \noindent {\large {\bfseries Bibliografische Information Der  
Deutschen
       Bibliothek}\\[3mm]
       Die Deutsche Bibliothek verzeichnet diese Publikation in der  
Deutschen
       Nationalbibliografie; detaillierte bibliografische Daten sind im
       Internet \"uber {\tt http://dnb.ddb.de} abrufbar.
       \vfill
       \noindent D7\\[1mm]
       Referent: \@refa\\[1mm]
       Korreferent: \@refb\\[1mm]
       Tag der m\"undlichen Pr\"ufung: \@exdate\\[30mm]
       ISBN \@isbn\\[5mm]
       Copernicus Publications \@pubyear\\[1mm]
       http://publications.copernicus.org\\[1mm]
       \copyright\ \@author\\[5mm]
       Printed in Germany\par}
    \fi
    \if@file
       \IfFileExists{secondpage.tex}{\include{secondpage}}
       {Please provide file secondpage.tex}
    \fi
\fi
\if@bs
    \if@sub
       \null
    \fi
    \if@acc
       \vspace*{150mm}
       \noindent {\large 1. Referentin oder Referent: \@refa\\[1mm]
       2. Referentin oder Referent: \@refb\\[1mm]
       eingereicht am: \@subdate\\[1mm]
       m\"undliche Pr\"ufung (Disputation) am: \@exdate\par}
    \fi
    \if@print
       \noindent {\large {\bfseries Bibliografische Information Der  
Deutschen
       Bibliothek}\\[3mm]
       Die Deutsche Bibliothek verzeichnet diese Publikation in der  
Deutschen
       Nationalbibliografie; detaillierte bibliografische Daten sind im
       Internet \"uber {\tt http://dnb.ddb.de} abrufbar.
       \vfill
       \noindent 1. Referentin oder Referent: \@refa\\[1mm]
       2. Referentin oder Referent: \@refb\\[1mm]
       eingereicht am: \@subdate\\[1mm]
       m\"undliche Pr\"ufung (Disputation) am: \@exdate\\[30mm]
       ISBN \@isbn\\[5mm]
       Copernicus Publications \@pubyear\\[1mm]
       http://publications.copernicus.org\\[1mm]
       \copyright\ \@author\\[5mm]
       Printed in Germany\par}
    \fi
    \if@file
       \IfFileExists{secondpage.tex}{\include{secondpage}}
       {Please provide file secondpage.tex}
    \fi
\fi
\if@goeorbs\else\IfFileExists{secondpage.tex}{\include{secondpage}}
{Please provide file secondpage.tex}\fi
} % end of maketitle definition
%%
\newenvironment{cfig}{\begin{figure}[t]\begin{center}}{\end{center} 
\end{figure}}
%%
\def\chaptername{}
\def\appendixname{}
%%
\pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{\thechapter\hskip2ex #1}
    {\thechapter\hskip2ex #1}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\hskip2ex #1}}
\fancyhf{}
\fancyhead[LE]{\nouppercase{\leftmark}}
\fancyhead[RO]{\nouppercase{\rightmark}}
\fancyfoot[LE,RO]{\thepage}
\renewcommand{\footrulewidth}{0pt}
\fancypagestyle{plain}{\fancyhf{}\fancyfoot[LE,RO]{\thepage}%
    \renewcommand{\headrulewidth}{0pt}\renewcommand{\footrulewidth} 
{0pt}}
%%
% avoids headings on otherwise empty pages before a new chapter
\def\cleardoublepage{\clearpage\if@twoside\ifodd\c@page\else
    \hbox{}\thispagestyle{empty}\newpage
    \if@twocolumn\hbox{}\newpage\fi\fi\fi}
%%
%\def\@schapter#1{\addcontentsline{toc}{chapter}{#1} % for toc
%   \@mkboth{#1}{#1}                                 % headings
%   \if@twocolumn\@topnewpage[\@makeschapterhead{#1}]
%   \else\@makeschapterhead{#1}\@afterheading\fi}
%
% problem: adds also toc to toc
%%
\def\@makechapterhead#1{\vspace*{50\p@}{\parindent\z@\raggedright
    \normalfont\interlinepenalty\@M\Huge\bfseries{%
    \@hangfrom{\hskip\z@\relax\thechapter\hskip2ex}#1\@@par}
    \par\nobreak\vskip40\p@}}
%%
%% End of file `thesis.cls'.

--Boundary_(ID_8vaiOHVH+3CE5q6BOg9/XQ)
Content-type: text/html; charset=US-ASCII
Content-transfer-encoding: quoted-printable

<html><body style=3D"word-wrap: break-word; -webkit-nbsp-mode: space; =
-webkit-line-break: after-white-space; "><div>Dear Axel =
Sommerfeldt,</div><div><br></div><div>I have read the documentation of =
the caption package, as I encountered a problem after the update from =
Mactex 2007 to Mactex 2009, thus using the version of the \caption =
package.</div><div><br></div><div>I am using a home-made "book"-based =
documentclass to write my Ph.D thesis, provided by the Max Planck =
Institute for Solar System Research in Germany. The class files are =
available there :&nbsp;</div><div><a =
href=3D"http://www.solar-system-school.de/thesis/thesis.zip">http://www.so=
lar-system-school.de/thesis/thesis.zip</a></div><div><br></div><div>If =
needed, at the end of this email I've copied-pasted the content of =
thesis.cls that I'm using (together with the copy of my document), so =
that you don't have to download the zip =
file.</div><div><br></div><div>With the older version, Mactex 2007, this =
exact bit is working fine. Since the update, the caption package no =
longer works, only the \caption2 package does. However, it doesn't offer =
some of the improvements that the current \caption offers, and which I =
need, thus I would like to make the later work. For instance, with =
\caption2, I would not know how to put the whole caption in italic, and =
not just the "figure #:", whereas it is possible with the current =
version of the caption package.</div><div><br></div><div>The bug report =
I have is not the expected warning (&nbsp;thus I thought I should report =
it) that you describe in your documentation =
:&nbsp;</div><div><br></div><div><div><i>Package caption Warning: =
Unsupported document class (or package) detected,</i></div> =
<div><i>(caption) usage of the caption package is not =
recommended.</i></div> <div><i>See the caption package documentation for =
explanation.</i></div></div><br><div>Instead, I have the following =
:&nbsp;</div><div><br></div><div>! Undefined control =
sequence.<br>\captionlabelfont@default =
-&gt;\cph@font</div><div><br></div><div>As it worked before with 2007 =
version, and also work now with \caption2, I understand it comes from =
the thesis.cls not being compatible =
anymore.&nbsp;</div><div><br></div><div>Would you know a solution =
?</div><div><br></div><div>Thank you for your =
help,</div><div><br></div><div><br></div><div><div>Raphael =
Attie</div><div><div><div>Ph.D Student</div><div>Max Planck Institute =
for Solar System Research</div><div>Max Planck Str. 2</div><div>37191 =
Katlenburg-Lindau</div><div>Germany</div><div><br></div></div></div></div>=
<div><br></div><div><div><br></div><div><br></div><div><br></div><div>Here=
 is a shortened version of my =
document.&nbsp;</div><div><br></div></div><div>------------------------</d=
iv><div><br></div><div><div>\documentclass[braunschweig]{thesis}</div><div=
><br></div><div>\usepackage{caption}</div><div>\usepackage[tight]{subfigur=
e}</div><div>\usepackage{epstopdf}</div><div>\usepackage{fixltx2e}</div><d=
iv>\usepackage{float}</div><div>\usepackage{amsmath}</div><div>\usepackage=
{txfonts}</div><div><br></div><div>\begin{document}</div><div><br></div><d=
iv>\section{Tracking the photospheric =
flows}</div><div><br></div><div>blablabla&nbsp;</div><div><br></div><div>\=
begin{figure*}[h]</div><div>\centering</div><div>\includegraphics[width=3D=
1 \textwidth]{./figures/photosphere1.jpeg}</div><div>\caption{Image of =
the solar photosphere in continuum with MDI/SoHO, with a close-up taken =
at higher resolution by FG-SOT/Hinode. The latter shows the =
granulation.} &nbsp;\label{granulation}</div><div>\end{figure*}<span =
class=3D"Apple-tab-span" style=3D"white-space:pre">	=
</span></div><div><br></div><div>\end{document}</div>---------------------=
---</div><div><br></div><div><br></div><div><br></div>--------------------=
---------<div><br></div><div><div>%% File: =
thesis.cls</div><div>%%</div><div>%% Author:</div><div>%% Dieter =
Schmitt</div><div>%% Max Planck Institute for Solar System =
Research</div><div>%% Max-Planck-Str. 2</div><div>%% D-37191 =
Katlenburg-Lindau</div><div>%% Germany</div><div>%%</div><div>%% Email: =
<a =
href=3D"mailto:schmitt@mps.mpg.de">schmitt@mps.mpg.de</a></div><div>%%</di=
v><div>%% For producing a PhD thesis for digital print and online =
publishing</div><div>%%&nbsp;</div><div>\NeedsTeXFormat{LaTeX2e}[1994/06/0=
1]</div><div>\def\MyProvidesClass#1 [#2 #3 =
#4]</div><div>&nbsp;&nbsp;{\ProvidesClass{#1}[#2 #3 =
#4]%</div><div>&nbsp;&nbsp; =
\def\clsname{#1}\def\clsdate{#2}\def\clsversion{#3}\def\clsinfo{#4}}</div>=
<div>\MyProvidesClass{thesis} [2008/07/22 1.8 =
(DS)]</div><div>%%</div><div>%% Version 1.2 (12 Jul 2005): change of =
Braunschweig title page, vec--&gt;vect, ...</div><div>%% Version 1.3 (01 =
Oct 2006): change of Braunschweig title page, txfonts, =
pdfoutput</div><div>%% Version 1.4 (22 Dec 2006): options =
nottoc,notlof,notlot added to tocbibind</div><div>%% Version 1.5 (17 Apr =
2007): change of Braunschweig title page</div><div>%% Version 1.6 (12 =
Oct 2007): Copernicus Publications and copyright</div><div>%% Version =
1.7 (05 Mar 2008): change of copyright</div><div>%% Version 1.8 (22 Jul =
2008): change of =
description</div><div>%%</div><div>\newif\if@goe</div><div>\newif\if@bs</d=
iv><div>\newif\if@goeorbs</div><div>\newif\if@sub</div><div>\newif\if@acc<=
/div><div>\newif\if@print</div><div>\newif\if@file</div><div>\newif\if@fem=
</div><div>\newif\if@german</div><div>\newif\if@hyper</div><div>\DeclareOp=
tion{goettingen}{\@goetrue\@goeorbstrue\@subtrue}</div><div>\DeclareOption=
{braunschweig}{\@bstrue\@goeorbstrue\@subtrue}</div><div>\DeclareOption{su=
bmitted}{\@subtrue}</div><div>\DeclareOption{accepted}{\@acctrue\@subfalse=
}</div><div>\DeclareOption{print}{\@printtrue\@subfalse}</div><div>\Declar=
eOption{file}{\@filetrue\@subfalse}</div><div>\DeclareOption{female}{\@fem=
true}</div><div>\DeclareOption{german}{\@germantrue}</div><div>\DeclareOpt=
ion{hyper}{\@hypertrue}</div><div>\DeclareOption*{\PassOptionsToClass{\Cur=
rentOption}{book}}</div><div>\ProcessOptions</div><div>\LoadClass[12pt]{bo=
ok}</div><div>%%</div><div>\ifx\pdfoutput\undefined\else</div><div>&nbsp;&=
nbsp; \setlength{\pdfpageheight}{29.7cm}</div><div>&nbsp;&nbsp; =
\setlength{\pdfpagewidth}{21.0cm}</div><div>\fi</div><div>\setlength{\pape=
rheight}{29.7cm}</div><div>\setlength{\paperwidth}{21.0cm}</div><div>\setl=
ength{\textheight}{23.5cm}</div><div>\setlength{\textwidth}{15.0cm}</div><=
div>\setlength{\headheight}{2.0cm}</div><div>\setlength{\headsep}{0.8cm}</=
div><div>\setlength{\topskip}{12pt}</div><div>\setlength{\footskip}{30pt}<=
/div><div>\setlength{\oddsidemargin}{0.46cm}</div><div>\setlength{\evensid=
emargin}{0.46cm}</div><div>\setlength{\topmargin}{-2.0cm}</div><div>%%</di=
v><div>\ifx\pdfoutput\undefined</div><div>&nbsp;&nbsp; =
\IfFileExists{graphicx.sty}{\RequirePackage[dvips]{graphicx}% =
LaTeX</div><div>&nbsp;&nbsp; =
\DeclareGraphicsExtensions{.eps,.ps}}{}</div><div>&nbsp;&nbsp; =
\IfFileExists{color.sty}{\RequirePackage{color}}{}</div><div>\else%</div><=
div>&nbsp;&nbsp; \ifnum\pdfoutput=3D0</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\IfFileExists{graphicx.sty}{\RequirePackage[dvips]{graphicx}% =
LaTeX</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\DeclareGraphicsExtensions{.eps,.ps}}{}</div><div>&nbsp;&nbsp; =
&nbsp; =
&nbsp;\IfFileExists{color.sty}{\RequirePackage{color}}{}</div><div>&nbsp;&=
nbsp; \else</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\IfFileExists{graphicx.sty}{\RequirePackage[pdftex]{graphicx}% =
pdfLaTeX</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\DeclareGraphicsExtensions{.pdf,.png,.jpg}}{}</div><div>&nbsp;&nbsp;=
 &nbsp; =
&nbsp;\IfFileExists{color.sty}{\RequirePackage[pdftex]{color}}{}</div><div=
>&nbsp;&nbsp; &nbsp; &nbsp;\pdfinfo{/Creator (thesis.cls version =
\clsversion)}</div><div>&nbsp;&nbsp; =
\fi</div><div>\fi</div><div>%%</div><div>%\IfFileExists{txfonts.sty}{\Requ=
irePackage{txfonts}}{}</div><div>\IfFileExists{natbib.sty}{\RequirePackage=
{natbib}}{}</div><div>\bibpunct{(}{)}{,}{a}{}{,}</div><div>%\setlength{\bi=
bsep}{0pt}</div><div>\IfFileExists{fancyhdr.sty}{\RequirePackage{fancyhdr}=
}{}</div><div>\IfFileExists{tocbibind.sty}{\RequirePackage[nottoc,notlof,n=
otlot]{tocbibind}}{}</div><div>\IfFileExists{fontenc.sty}{\RequirePackage[=
T1]{fontenc}}{}</div><div>\IfFileExists{url.sty}{\RequirePackage{url}}{}</=
div><div>\IfFileExists{amssymb.sty}{\RequirePackage{amssymb}}{}</div><div>=
%\IfFileExists{amsmath.sty}{\RequirePackage{amsmath}}{}</div><div>\IfFileE=
xists{ifthen.sty}{\RequirePackage{ifthen}}{}</div><div>\IfFileExists{array=
sty}{\RequirePackage{array}}{}</div><div>\IfFileExists{multicol.sty}{\Req=
uirePackage{multicol}}{}</div><div>%%</div><div>\if@german</div><div>&nbsp=
;&nbsp; =
\IfFileExists{german.sty}{\RequirePackage{german}}{}</div><div>&nbsp;&nbsp=
; \def\captionsgerman{%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\acknowname{Danksagung}%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\refname{Literaturverzeichnis}%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\abstractname{Zusammenfassung}%</div><div>% &nbsp; &nbsp; =
\def\appendixname{Anhang}%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\figurename{Abbildung}%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\tablename{Tabelle}}</div><div>&nbsp;&nbsp; =
\selectlanguage{german}</div><div>\else</div><div>&nbsp;&nbsp; =
\def\captionsenglish{%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\acknowname{Acknowledgement}%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\refname{References}%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\abstractname{Abstract}%</div><div>% &nbsp; &nbsp; =
\def\appendixname{Appendix}%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\figurename{Figure}%</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\def\tablename{Table}}</div><div>\fi</div><div>%%</div><div>\if@hype=
r\IfFileExists{hyperref.sty}{\RequirePackage{hyperref}}{}\fi</div><div>%%<=
/div><div>\DeclareRobustCommand*{\vect}[1]{\ensuremath{%</div><div>\mathch=
oice{\mbox{\boldmath$\displaystyle#1$}}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp; &nbsp; &nbsp; =
{\mbox{\boldmath$\textstyle#1$}}</div><div>&nbsp;&nbsp; &nbsp; &nbsp; =
&nbsp; &nbsp; {\mbox{\boldmath$\scriptstyle#1$}}</div><div>&nbsp;&nbsp; =
&nbsp; &nbsp; &nbsp; &nbsp; =
{\mbox{\boldmath$\scriptscriptstyle#1$}}}}</div><div>%%</div><div>\Declare=
RobustCommand*{\chem}[1]{\ensuremath{\mathrm{#1}}}</div><div>\DeclareRobus=
tCommand*{\unit}[1]{\def~{\,}\ensuremath{\mathrm{#1}}}</div><div>%%</div><=
div>\setcounter{topnumber}{2}</div><div>\def\topfraction{1.}</div><div>\se=
tcounter{bottomnumber}{1}</div><div>\def\bottomfraction{1.}</div><div>\set=
counter{totalnumber}{3}</div><div>\def\textfraction{0.}</div><div>\def\flo=
atpagefraction{.7}</div><div>\setcounter{secnumdepth}{3}</div><div>\setcou=
nter{tocdepth}{3}</div><div>%%</div><div>%\sloppy\clubpenalty4000\widowpen=
alty4000</div><div>%%</div><div>\def\town#1{\def\@town{#1}} &nbsp; =
&nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; =
\def\@town{???}</div><div>\def\refereea#1{\def\@refa{#1}} &nbsp; &nbsp; =
&nbsp; &nbsp; &nbsp; =
\def\@refa{???}</div><div>\def\refereeb#1{\def\@refb{#1}} &nbsp; &nbsp; =
&nbsp; &nbsp; &nbsp; =
\def\@refb{???}</div><div>\def\submitteddate#1{\def\@subdate{#1}} &nbsp; =
\def\@subdate{???}</div><div>\def\submittedyear#1{\def\@subyear{#1}} =
&nbsp; =
\def\@subyear{\number\year}</div><div>\def\examinationdate#1{\def\@exdate{=
#1}} =
&nbsp;\def\@exdate{???}</div><div>\def\publicationyear#1{\def\@pubyear{#1}=
} \def\@pubyear{\number\year}</div><div>\def\isbn#1{\def\@isbn{#1}} =
&nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; =
\def\@isbn{???}</div><div>%%</div><div>\def\maketitle{%</div><div>\begin{t=
itlepage}</div><div>\if@goe</div><div>&nbsp;&nbsp; =
\vspace*{20mm}</div><div>&nbsp;&nbsp; =
\begin{center}</div><div>&nbsp;&nbsp; =
{\Huge\bfseries\@title\par}</div><div>&nbsp;&nbsp; =
\vspace{30mm}</div><div>&nbsp;&nbsp; {\large =
Dissertation\\[1mm]</div><div>&nbsp;&nbsp; zur Erlangung des =
Doktorgrades\\[1mm]</div><div>&nbsp;&nbsp; der =
Mathematisch-Naturwissenschaftlichen =
Fakult\"aten\\[1mm]</div><div>&nbsp;&nbsp; der =
Georg-August-Universit\"at zu G\"ottingen</div><div>&nbsp;&nbsp; =
\vfill</div><div>&nbsp;&nbsp; vorgelegt =
von\\[1mm]</div><div>&nbsp;&nbsp; =
{\Large\bfseries\@author}\\[1mm]</div><div>&nbsp;&nbsp; aus =
\@town</div><div>&nbsp;&nbsp; \par\vspace{30mm}</div><div>&nbsp;&nbsp; =
G\"ottingen \space\@subyear}</div><div>&nbsp;&nbsp; =
\end{center}</div><div>\fi</div><div>\if@bs</div><div>&nbsp;&nbsp; =
\if@sub</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vspace*{10mm}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\begin{center}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;{\Huge\bfseries\@title\par}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vspace{20mm}</div><div>&nbsp;&nbsp; &nbsp; &nbsp;{\large Der =
Fakult\"at f\"ur Elektrotechnik, Informationstechnik, =
Physik\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;der Technischen =
Universit\"at Carolo-Wilhelmina\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;zu Braunschweig\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;zur =
Erlangung des Grades \if@fem einer \else eines \fi =
\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\if@fem Doktorin \else =
Doktors \fi der Naturwissenschaften\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;(Dr.rer.nat.)\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;eingereichte\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;Dissertation</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\par\vspace{30mm}</div><div>&nbsp;&nbsp; &nbsp; &nbsp;von =
\@author\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;aus =
\@town\par}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\end{center}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vfill</div><div>&nbsp;&nbsp; &nbsp; &nbsp;{\large 1. Referentin =
oder Referent: \@refa\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;2. =
Referentin oder Referent: \@refb\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;eingereicht am: \@subdate\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;m\"undliche Pr\"ufung (Disputation) =
am:\par}</div><div>&nbsp;&nbsp; \else</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vspace*{20mm}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\begin{center}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;{\Huge\bfseries\@title\par}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vspace{30mm}</div><div>&nbsp;&nbsp; &nbsp; &nbsp;{\large Von der =
Fakult\"at f\"ur Elektrotechnik, Informationstechnik, =
Physik\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;der Technischen =
Universit\"at Carolo-Wilhelmina\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;zu Braunschweig\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;zur =
Erlangung des Grades \if@fem einer \else eines \fi =
\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\if@fem Doktorin \else =
Doktors \fi der Naturwissenschaften\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;(Dr.rer.nat.)\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;genehmigte\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;Dissertation</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\par\vspace{30mm}</div><div>&nbsp;&nbsp; &nbsp; &nbsp;von =
\@author\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;aus =
\@town\par}</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\end{center}</div><div>&nbsp;&nbsp; =
\fi</div><div>\fi</div><div>\if@goeorbs\else\IfFileExists{firstpage.tex}{\=
include{firstpage}}</div><div>&nbsp;&nbsp; {Please provide file =
firstpage.tex}\fi</div><div>\end{titlepage}</div><div>\newpage % second =
page</div><div>\thispagestyle{empty}</div><div>\if@goe</div><div>&nbsp;&nb=
sp; \if@sub</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vspace*{150mm}</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\noindent =
{\large D7\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Referent: =
\@refa\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Korreferent: =
\@refb\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Tag der m\"undlichen =
Pr\"ufung: \par}</div><div>&nbsp;&nbsp; \fi</div><div>&nbsp;&nbsp; =
\if@print</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\noindent {\large =
{\bfseries Bibliografische Information Der =
Deutschen&nbsp;</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;Bibliothek}\\[3mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Die =
Deutsche Bibliothek verzeichnet diese Publikation in der =
Deutschen&nbsp;</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;Nationalbibliografie; detaillierte bibliografische Daten sind =
im&nbsp;</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Internet \"uber {\tt <a =
href=3D"http://dnb.ddb.de">http://dnb.ddb.de</a>} =
abrufbar.</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vfill</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\noindent =
D7\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Referent: =
\@refa\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Korreferent: =
\@refb\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Tag der m\"undlichen =
Pr\"ufung: \@exdate\\[30mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;ISBN =
\@isbn\\[5mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Copernicus =
Publications \@pubyear\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;<a =
href=3D"http://publications.copernicus.org">http://publications.copernicus=
org</a>\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\copyright\ =
\@author\\[5mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Printed in =
Germany\par}</div><div>&nbsp;&nbsp; \fi</div><div>&nbsp;&nbsp; =
\if@file</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\IfFileExists{secondpage.tex}{\include{secondpage}}</div><div>&nbsp;=
&nbsp; &nbsp; &nbsp;{Please provide file =
secondpage.tex}</div><div>&nbsp;&nbsp; =
\fi</div><div>\fi</div><div>\if@bs</div><div>&nbsp;&nbsp; =
\if@sub</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\null</div><div>&nbsp;&nbsp; =
\fi</div><div>&nbsp;&nbsp; \if@acc</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vspace*{150mm}</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\noindent =
{\large 1. Referentin oder Referent: =
\@refa\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;2. Referentin oder =
Referent: \@refb\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;eingereicht =
am: \@subdate\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;m\"undliche =
Pr\"ufung (Disputation) am: \@exdate\par}</div><div>&nbsp;&nbsp; =
\fi</div><div>&nbsp;&nbsp; \if@print</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\noindent {\large {\bfseries Bibliografische Information Der =
Deutschen&nbsp;</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;Bibliothek}\\[3mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Die =
Deutsche Bibliothek verzeichnet diese Publikation in der =
Deutschen&nbsp;</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;Nationalbibliografie; detaillierte bibliografische Daten sind =
im&nbsp;</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Internet \"uber {\tt <a =
href=3D"http://dnb.ddb.de">http://dnb.ddb.de</a>} =
abrufbar.</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\vfill</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\noindent 1. Referentin =
oder Referent: \@refa\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;2. =
Referentin oder Referent: \@refb\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;eingereicht am: \@subdate\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;m\"undliche Pr\"ufung (Disputation) am: =
\@exdate\\[30mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;ISBN =
\@isbn\\[5mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Copernicus =
Publications \@pubyear\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;<a =
href=3D"http://publications.copernicus.org">http://publications.copernicus=
org</a>\\[1mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;\copyright\ =
\@author\\[5mm]</div><div>&nbsp;&nbsp; &nbsp; &nbsp;Printed in =
Germany\par}&nbsp;</div><div>&nbsp;&nbsp; \fi</div><div>&nbsp;&nbsp; =
\if@file</div><div>&nbsp;&nbsp; &nbsp; =
&nbsp;\IfFileExists{secondpage.tex}{\include{secondpage}}</div><div>&nbsp;=
&nbsp; &nbsp; &nbsp;{Please provide file =
secondpage.tex}</div><div>&nbsp;&nbsp; \fi =
&nbsp;</div><div>\fi</div><div>\if@goeorbs\else\IfFileExists{secondpage.te=
x}{\include{secondpage}}</div><div>{Please provide file =
secondpage.tex}\fi</div><div>} % end of maketitle =
definition</div><div>%%</div><div>\newenvironment{cfig}{\begin{figure}[t]\=
begin{center}}{\end{center}\end{figure}}</div><div>%%</div><div>\def\chapt=
ername{}</div><div>\def\appendixname{}</div><div>%%</div><div>\pagestyle{f=
ancy}</div><div>\renewcommand{\chaptermark}[1]{\markboth{\thechapter\hskip=
2ex #1}</div><div>&nbsp;&nbsp; {\thechapter\hskip2ex =
#1}}</div><div>\renewcommand{\sectionmark}[1]{\markright{\thesection\hskip=
2ex =
#1}}</div><div>\fancyhf{}</div><div>\fancyhead[LE]{\nouppercase{\leftmark}=
}</div><div>\fancyhead[RO]{\nouppercase{\rightmark}}</div><div>\fancyfoot[=
LE,RO]{\thepage}</div><div>\renewcommand{\footrulewidth}{0pt}</div><div>\f=
ancypagestyle{plain}{\fancyhf{}\fancyfoot[LE,RO]{\thepage}%</div><div>&nbs=
p;&nbsp; =
\renewcommand{\headrulewidth}{0pt}\renewcommand{\footrulewidth}{0pt}}</div=
><div>%%</div><div>% avoids headings on otherwise empty pages before a =
new =
chapter</div><div>\def\cleardoublepage{\clearpage\if@twoside\ifodd\c@page\=
else</div><div>&nbsp;&nbsp; =
\hbox{}\thispagestyle{empty}\newpage</div><div>&nbsp;&nbsp; =
\if@twocolumn\hbox{}\newpage\fi\fi\fi}</div><div>%%</div><div>%\def\@schap=
ter#1{\addcontentsline{toc}{chapter}{#1} % for toc</div><div>% &nbsp; =
\@mkboth{#1}{#1} &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; =
&nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; &nbsp; % =
headings</div><div>% &nbsp; =
\if@twocolumn\@topnewpage[\@makeschapterhead{#1}]</div><div>% &nbsp; =
\else\@makeschapterhead{#1}\@afterheading\fi}</div><div>%</div><div>% =
problem: adds also toc to =
toc</div><div>%%</div><div>\def\@makechapterhead#1{\vspace*{50\p@}{\parind=
ent\z@\raggedright</div><div>&nbsp;&nbsp; =
\normalfont\interlinepenalty\@M\Huge\bfseries{%</div><div>&nbsp;&nbsp; =
\@hangfrom{\hskip\z@\relax\thechapter\hskip2ex}#1\@@par}</div><div>&nbsp;&=
nbsp; \par\nobreak\vskip40\p@}}</div><div>%%</div><div>%% End of file =
`thesis.cls'.</div><br></div></body></html>=

--Boundary_(ID_8vaiOHVH+3CE5q6BOg9/XQ)--
\fi

\errorcontextlines=9
\PassOptionsToPackage{demo}{graphicx}
\documentclass[braunschweig]{thesis}

\usepackage{caption}

%\usepackage[tight]{subfigure}
%\usepackage{epstopdf}
%\usepackage{fixltx2e}
%\usepackage{float}
%\usepackage{amsmath}
%\usepackage{txfonts}

\begin{document}

\section{Tracking the photospheric flows}

blablabla

\begin{figure*}[h]
\centering
\includegraphics[width=1 \textwidth]{./figures/photosphere1.jpeg}
\caption{Image of the solar photosphere in continuum with MDI/SoHO,  
with a close-up taken at higher resolution by FG-SOT/Hinode. The  
latter shows the granulation.}  \label{granulation}
\end{figure*}

\end{document}

### 2017-04-24 paper.tex
added caption package, figures and edited paper

@@
 \usepackage{pifont}
+\usepackage{caption}
+\usepackage{graphicx}
+\usepackage{wrapfig,lipsum,booktabs}
+\captionsetup{justification=raggedright,singlelinecheck=false}
+\providecommand{\keywords}[1]{\textbf{Keywords} #1}
 \begin{document}
@@
 \begin{abstract}
-TODO: Abstract
+In GUI applications, a user interacts with the system via graphical interface such as mouse click, scroll, drag, text box etc.
+There could be large number of possible sequences in which a user can interact.
+Testing such application means ensuring the correct sequence of interactions resulting in desired output.
+If this testing is done manually, it could be tedious.
+Therefore, capture and replay tools came into existence.
+It  enables the testers to record the entire ineteractive session and replaying it at any later time.
+By replaying a given log file on a changed version of the application, capture and replay tools thus support fully-automatic regression testing of graphical user interfaces.
 \end{abstract}
+
+\keywords\\{GUI testing; capture and replay tools; Reanimator}
 
@@
 \IEEEPARstart{S}{oftware} testing is a process of  evaluating the software for its functionality by performing some test cases on an attribute or capability of a program or system and determining that it meets its required results.
-Software testing involves the execution of a software component or system component to evaluate one or more properties of interest.
-Testing the graphical user interface (GUI) of a software product is important to ensure the quality of the system and therefore to improve the user satisfaction of using the software\cite{Nedyalkova:2013:OSC:2494444.2494464}.
-But testing GUI is tedious and time consuming because it requires a sequence of user interactions.
-There are special tools available to test such software.
-These tools are called capture and replay tools.
-They capture a sequence of interactions which can be replayed at a later time for testing.
+It involves the execution of a software component or system component to evaluate one or more properties of interest.
+Testing the graphical user interface (GUI) of a software product is important to ensure the quality of the system and therefore to improve the user experience\cite{Nedyalkova:2013:OSC:2494444.2494464}.
+It not only involves testing the GUI but also the functionality of system.
+But manual testing GUI is tedious and time consuming.
+GUI capture and replay tools was  developed as a mechanism for testing the correctness of interactive applications with graphical user interfaces.
+Using a capture and replay tool, a tester can run an application and record the entire interactive session.
+The tool records all the user's events, such as the keys pressed or the mouse movements, in a log file called test scripts.
+Given tets scripts, the tool can then automatically replay the exact same interactive session any number of times without requiring a human user.
+This helps in early detection of bugs that might lead to system failure and therefore speed up the process of development.\\
+The advantages of using capture and replay tools is that it saves time by making the process easy and quick.
+They save the time of hand-coding test scripts.
+They also make it simple for testers without significant programming skills to automate their test case \cite{Memom}.
+However, these tools also have some drawbacks.
+They don’t generate test cases automatically; sometimes the recorded test scripts are inefficient and require manual intervention; the tools know only how to interact with widgets, but they have no idea what application they are operating on \cite{Silverstein}; in regression testing any change in the GUI may cause a test case to break or stop to execute against the updated version \cite{Memom}.\\
+In this paper we compare four capture and replay tools on different criteria.
+This comparison study will be helpful for the developers to choose the capture and replay tool that would be best fit for testing their applications.
+Further we extended Reanimator, an existing capture and replay tool, and enhanced it by adding functionality that will help web developers to actually use it in field.\\
+ The remainder of this paper is organized as follows.
+Section 2 discusses about the previous work done in this field, Section 3 discusses about the tools that were used for the comparison, Section 4 decribes the evaluation criteria used to establish the comparison, Section 5 includes analysis of comparison, Section 6 describes in detail about the extension of Reanimator.
+Finally, in Section 7 we concluded the paper by presenting a short summary.
 
-\section{Previous Work}
-Nedyalkova and  Bernardino established a comparison of capture and replay tools.
+\section{Literature Review}
+Nedyalkova and  Bernardino \cite{comparison survey} established a comparison of capture and replay tools.
 They evaluated five open source capture and replay tools namely Abbot, Jacareto, JFCUnit, Marathon and Pounder.
@@
 Based on the results, they found out that Jacareto is the best tool among all five evaluated.
-Jacareto is easy to install, had better documentation, does not require additionally programming skills, supports all capture and replay characteristics except for navigation of dialog box.
+Jacareto is easy to install, had better documentation, does not require additional programming skills, supports all capture and replay characteristics except for navigation of dialog box.
 It allows tester to replay the test script in a speed that facilitates to observe the actions \cite{Nedyalkova:2013:OSC:2494444.2494464}.
 
-Similarly, Rodrigues et al.
-performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
+Similarly, Rodrigues et al.\cite{paper 2} performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
 They studied the effort required (time spent) to use CR-based and MBT tools.
@@
 
-Mugshot is a deterministic capture and replay tool developed by Microsoft.
-It captures every event in  that is executed in JavaScript program which can be replayed deterministically at any later time to analyze the sequence of events that might have led to system failure.
+Mugshot\cite{Mugshot} is a deterministic capture and replay tool developed by Microsoft.
+It captures every event that is executed in JavaScript program which can be replayed deterministically at any later time to analyze the sequence of events that might have led to system failure.
 To capture application activity, it records all sources of nondeterminism.
@@
 \section{Description of Capture and Replay Tools Used}
+In this section, we give a short description of capture and replay tools used in this study.
+We focused on those capture and replay tools that are built for internet applications.
+Here, we compared four tools $-$ Reanimator, Sahi, Telerik and Selenium IDE.
+Following is the description of these tools:
 \subsection{Reanimator}
-Reanimator\footnote{https://github.com/WaterfallEngineering/reanimator} captures non-deterministic input to a JavaScript application in a log that can replayed at a later date.
+Reanimator\footnote{https://github.com/WaterfallEngineering/reanimator} captures non-deterministic input to a JavaScript application in a log that can be replayed at a later time.
 It was originally designed for recording web application crashes in the wild for later debugging.
@@
 It works only on Firefox.
-It supports both Windows and Linux platforms.
+It supports both Windows and Linux platforms.Reanimator consists of a core, which is responsible for capture setup and driving the replay, and one or more plugins, which are responsible for capturing and replaying non-deterministic input.
+Reanimator ships with plugins for capturing and replaying random numbers, dates, and timer interrupts.
 
@@
 There are two versions of Sahi tool: one is open source and is available on SourceForge and proprietary version called Sahi Pro which is available on their official website.
-Open source comes with basic record and replay functionalities written in Java and JavaScript.
+It has powerful abilities for recording and replaying across browsers; different language drivers for writing test scripts (Java, Ruby); and support for AJAX and highly dynamic web applications.
+Sahi also supports https and NTLM authentications.
 It works on Internet Explorer, Firefox and Chrome.
 It only supports Windows platform.
+Following figure shows how Sahi fits in a simulated user operation.
+\begin{figure}[h!]
+ \hfill\includegraphics[width=9cm]{figures/sahi.PNG}\hspace*{\fill}
+ \caption{Simulated user operation}
+ \label{fig}
+\end{figure}
 
@@
 It works on Internet Explorer, Firefox, Chrome and Safari.
+It has features like visual storyboard and 3D element selection.
+It also offers script-lesstest automation for Silverlight applications.Test Studio offers three product versions:\\
+1. The Functional version performs web and WPF testing and includes the Visual Studio plugin.\\
+2. The Load version performs load testing.\\
+3. The Ultimate version combines Web, Mobile, WPF, Load testing and Test Studio for APIs.\\
 
@@
 It includes the entire Selenium Core which allows easy and quick record and play back tests in the actual environment that they will run in.
-It supports both Windows and Linux platforms.
+It supports both Windows and Linux platforms.Selenium IDE supports autocomplete mode when creating tests.
+This feature serves two purposes:\\
+$\bullet$ It helps the tester to enter commands more quickly.\\
+$\bullet$ It restricts the user from entering invalid commands.\\
 
 \section{Evaluation of Existing Tools}
-We focused on capture and replay tools that are built for internet applications.
-Here, we compared four tools – Reanimator, Sahi, Telerik and Selenium IDE.
-The tools are installed on an HP laptop with Intel core i5 processor (2.30 GHz), 4 GB RAM and windows 8.1 operating system with Java 1.8.
+ The four tools discussed in previous section are installed on an HP laptop with Intel core i5 processor (2.30 GHz), 4 GB RAM and windows 8.1 operating system with Java 1.8.
 We installed the tools Sahi, Telerik and Selenium.
 The code for Reanimator was directly deployed on a web server we manage.
-The following criteria are used to establish comparison between these tools:
+Initially, to test these tools (except for Reanimator) a simple online calculator written in Javascript is deployed at 1.eecs493.pollack.tech/index1.html.
+Reanimator demo comes with a tile game.
+We used the same tile game to test Reanimator which is available at 1.eecs493.pollack.tech.\\
+The following criteria are used to establish comparison between these tools:\\ \\
+\textbf{ \textit{Evaluation for ease of deployment:}}
 \begin{enumerate}
@@
 \item Examples provided
-\item User interface for developers
+\item User interface for developers\\
 \end{enumerate}
-Level of detail of measurements:
+\textbf{\textit{Evalution for level of detail of measurements:}}
 \begin{enumerate}
@@
 \item Scrolling
-\item Dialog box
+\item Dialog box\\
 \end{enumerate}
-System Information:
+\textbf{\textit{Additional system information:}}
 \begin{enumerate}
@@
 \item Browser support
-\item Additional features
+\item Additional features\\
 \end{enumerate}
 
-\begin{table*}[b]
-\centering
-\begin{tabular}{ | c | c | c | c | c | }
-\hline
-Characteristic            & Reanimator  & Sahi  & Telerik & Selenium IDE \\
-\hline
-Easy to Install           & X & \ding{51} & \ding{51} & \ding{51} \\
-\hline
-Time Required to Install  & Very Quick & Quick & Very Long and Tedious & Quick \\
-\hline
-User Interface            & X & \ding{51} & \ding{51} & \ding{51} \\
-\hline
-Easy to Use               & X & \ding{51} & \ding{51} & \ding{51} \\
-\hline
-Documentaion              & X & \ding{51} & \ding{51} & \ding{51} \\
-\hline
-Tutorial                  & X & X & \ding{51} & \ding{51} \\
-\hline
-Open Source               & \ding{51} & \ding{51} & X & \ding{51} \\
-\hline
-Examples                  & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
-\hline
-Programming Skills        & \ding{51} & X & X & X \\
-\hline
+The modified version of Reanimator is deployed at 2.eecs493.pollack.tech. The developer can select the recorded session to be played from drop down list available.  
+Table 1 shows the comparison between Reanimator, Sahi, Telerik  and Selenium based on criteria for evalution for ease of deployment.Table 2 shows the comparison  based on criteria for evalution for level of detail of measurements.Table 3 shows the additiona system information provided with each tool.
+The symbol \ding{51} means that the tool provides the characteristic which is in evaluation and the symbol \ding{55} means that it doesn’t support it.
+\\
 
-\end{tabular}
-\caption{Caption.}
-\end{table*}
+%\begin{wraptable}{r}{6.5cm}
+\begin{figure}[h!]
+ \hfill\includegraphics[width=9cm]{figures/table1.PNG}\hspace*{\fill}
+\end{figure}
+\begin{figure}[h!]
+ \hfill\includegraphics[width=9cm]{figures/table2.PNG}\hspace*{\fill}
+\end{figure}
 
-\begin{table*}[b]
-\centering
-\begin{tabular}{ | c | c | c | c | c | }
-\hline
-Characteristic            & Reanimator  & Sahi  & Telerik & Selenium IDE \\
-\hline
-Mouse Click               & \ding{51} & \ding{51} & \ding{51} & \ding{51} \\
-\hline
-Text Field                & X & \ding{51} & \ding{51} & \ding{51} \\
-\hline
-Mouse Drags               & X & X & X & X \\
-\hline
-Mouse Move                & X & X & X & X \\
-\hline
-Scrolling                 & X & X & X & X \\
-\hline
-Dialog Box                & X & \ding{51} & \ding{51} & \ding{51} \\
-\hline
-
-\end{tabular}
-\caption{Caption.}
-\end{table*}
+\begin{figure}[h!]
+ \hfill\includegraphics[width=9cm]{figures/table3.PNG}\hspace*{\fill}
+\end{figure}
 
 \section{Comparison Analysis}
-All the tools are good at capturing and replaying task.
+The tools used here does their work of capturing and replaying the interactive sessions.
 But while taking other criteria into consideration, Sahi performs better than the other tools.
-It has very easy and quick installation.
-It has very well documentation and tutorials available online.
+Compared to Telerik and Reanimator, Sahi has easier installation.
+It has strong documentation available online.
 It does not require any programming skill to use Sahi.
-Selenium also provides all these features but it can only be used to capture and replay Firefox sessions.
-It allows the user to set speed to analyse the scenarios.
+Sahi supports Chrome, Firefox and Internet Explorer.
+Selenium is easiest to install as it comes as firefox plugin.
+It also provides all the features like Sahi but the greatest setback of selenium is that it can only be used to capture and replay Firefox sessions.
+It has a great feature that allows the user to set speed to analyse the scenarios.
+No other tool provides this feature and has their own replay speed.
+This makes the process of analysis cumbersome if the default speed is very fast or slow.
 Telerik has a major setback that its installation takes very long (it took us 1 day to install) to finish since it requires lot of dependencies and also its installation process is not very effective.
 It requires large hard disk space.
-It has the feature called storyboard which is the snapshot of each scenario.
+It has the feature called visual storyboard which gives the snapshot of each scenario recorded by tool.
+This allows the developer to go to any snapshot.
+We used the one month free trial version of Telerik and requires to purchase once the trial period expires.
+Telerik also supports Chrome, Firefox and Internet Explorer.
 Reanimator is a small capture and replay tool inspired by Mugshot.
 It requires programming skills since it does not come as ready to use testing tool.
-It is built on JQuery 1.8.3 and works only on Firefox.
-In our further work, we upgraded it to JQuery 3.2.0 and enabled it to work on Chrome too.
+It is built on JQuery 1.8.3.
+It requires programming skills to get Reanimator working.Also it works only on Firefox and Internet Explorer.
+It does not have any additional feauture.
+\\
+We modified Reanimator by upgrading it to JQuery 3.2.0 and enabled it to work on Chrome too.
+It could be seen that the old version of Reanimator provided by the developers which is available at 1.eecs493.pollack.tech does not work on Chrome.
+While the modified version does work on Chrome.
+Reanimator comes with a demo which is a tile game.
+We have used the same game to test the modified version.
+ Based on the evalution criteria seen in table 1, 2 and 3, we choose Sahi as the best tool among all others.
 

### 2017-04-24 caption/2ctan.sh

@@ -1,0 +1,36 @@
+#!/bin/sh
+#
+# 2011-10-09: 1st version
+# 2011-10-10: Log file will be copied as ".LOG" now (needs package "mmv")
+# 2011-11-06: File CHANGELOG added to distribution
+# 2012-03-15: Option "-p" added to "cp" command
+# 2013-01-08: "-U dante" changed to "-u http://www.ctan.org/upload"
+# 2013-02-03: Adapted to new SVN directory structure
+# 2015-09-17: Revised, ctanupload commented out since currently-not-working
+#
+# Needs on CentOS/Fedora: mmv perl-File-Copy-Recursive perl-HTML-FormatText* perl-WWW-Mechanize* perl-XML-TreeBuilder
+#
+dist_dir=$(pwd)
+#
+rm -fr /tmp/caption
+mkdir /tmp/caption
+cp -a source/*.ins source/*.dtx source/*.tex source/*.eps /tmp/caption
+cp -a tex/*.sty /tmp/caption
+cp -a doc/README doc/CHANGELOG doc/SUMMARY doc/*.pdf /tmp/caption
+cd /tmp/caption
+ctanify caption.ins "*.tex=source/latex/caption" "*.eps=source/latex/caption" README "CHANGELOG=doc/latex/caption" "SUMMARY=doc/latex/caption" *.pdf
+#
+if [ $? -eq 0 ]; then
+  cp -a /tmp/caption/caption.tar.gz $dist_dir/caption_$(date --rfc-3339=date).tar.gz
+  cd $dist_dir
+
+#  ctanupload -l -p -u http://www.ctan.org/upload \
+#    --contribution=caption \
+#    --name "Axel Sommerfeldt" --email axel.sommerfeldt@f-m.fm \
+#    --summary-file $dist_dir/doc/SUMMARY \
+#    --directory=/macros/latex/contrib/caption \
+#    --DoNotAnnounce=0 \
+#    --license=free --freeversion=lppl \
+#    --file=/tmp/caption/caption.tar.gz
+fi
+

### 2017-04-25 paper.tex
edited author and added conclusion

@@
 \documentclass[12pt,journal]{IEEEtran}
-\usepackage[
-  backend=biber,
-  style=numeric,
-  citestyle=numeric
-]{biblatex}
-\addbibresource{citations.bib}
+\usepackage{biblatex}
+%[  backend=biber, style=numeric,  citestyle=numeric]
+%\usepackage{cite}
+\addbibresource{ref.bib}
+%\bibliography{ref}
+%\bibliographystyle{IEEEtran}
 \usepackage{pifont}
@@
 \usepackage{graphicx}
-\usepackage{wrapfig,lipsum,booktabs}
+\usepackage{wrapfig,booktabs}
+\usepackage{authblk}
+\usepackage{biblatex}
 \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 \title{Capture and Replay Tools in the Field}
-\author{Deepa Chhetri and Brian Pollack}
+\author[1]{Deepa Chhetri}
+\author[1]{Brian Pollack}
+\affil[1]{Department of EECS, Case Western Reserve University}
 \maketitle
@@
 It involves the execution of a software component or system component to evaluate one or more properties of interest.
-Testing the graphical user interface (GUI) of a software product is important to ensure the quality of the system and therefore to improve the user experience\cite{Nedyalkova:2013:OSC:2494444.2494464}.
+Testing the graphical user interface (GUI) of a software product is important to ensure the quality of the system and therefore to improve the user experience\cite{paper}.
 It not only involves testing the GUI but also the functionality of system.
@@
 \section{Literature Review}
-Nedyalkova and  Bernardino \cite{comparison survey} established a comparison of capture and replay tools.
+Nedyalkova and  Bernardino \cite{paper} established a comparison of capture and replay tools.
 They evaluated five open source capture and replay tools namely Abbot, Jacareto, JFCUnit, Marathon and Pounder.
-The criteria that they used for comparison is divided into two major groups - ``General Characteristics'' and ``Capture/Replay Characteristics''.
+The criteria that they used for comparison is divided into two major groups - "General Characteristics'' and "Capture/Replay Characteristics''.
 General characteristics include:
@@
 Jacareto is easy to install, had better documentation, does not require additional programming skills, supports all capture and replay characteristics except for navigation of dialog box.
-It allows tester to replay the test script in a speed that facilitates to observe the actions \cite{Nedyalkova:2013:OSC:2494444.2494464}.
+It allows tester to replay the test script in a speed that facilitates to observe the actions \cite{paper}.
 
-Similarly, Rodrigues et al.\cite{paper 2} performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
+Similarly, Rodrigues et al.\cite{paper2} performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
 They studied the effort required (time spent) to use CR-based and MBT tools.
@@
 They summarize the result by giving average time spent per treatment to complete each session.
-They found out that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly \cite{Rodrigues:2014:ECR:2652524.2652587}.
+They found out that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly \cite{paper2}.
 
-Mugshot\cite{Mugshot} is a deterministic capture and replay tool developed by Microsoft.
+Mugshot\cite{paper4} is a deterministic capture and replay tool developed by Microsoft.
 It captures every event that is executed in JavaScript program which can be replayed deterministically at any later time to analyze the sequence of events that might have led to system failure.
@@
 The entry also contains the event type and enough type-specific data to recreate event at play time.
-Mugshot uses a caching proxy to reproduce the load events in the log \cite{Mickens:2010:MDC:1855711.1855722}.
+Mugshot uses a caching proxy to reproduce the load events in the log \cite{paper4}.
 This is the limitation of Mugshot.
@@
 
+\section{Conclusion}
+In our study, we compared four capture and replay tools, namely Reanimator, Sahi, Telerik and Selenium.
+The goal of this study was to determine the best tool among these which has best overall performance.
+These tools were compared on different criteria to find out which tool has reliable capture and replay capabilities without requiring too much human efforts.
+After evaluating each one of the tools, we came to a conclusion that the tool that best satisfies our requirements is Sahi.
+This tool stood out from rest of the tools as it has best overall performance.
+Therefore, we can say that Sahi can be easily adapted by any developer to test their GUI application.
+We also worked on Reanimator to enhance it by additing new functionalities to it.
+We enabled it to work on Chrome.
+We ...{to be added by Brian}
+
+%\bibliographystyle{IEEEtran}
+
 \printbibliography

### 2017-04-26 paper.tex
Update paper.tex
Updated citations, minor formatting updates

--- 2017-04-24 paper.tex
@@
 style=numeric,
-  citestyle=numeric
-]{biblatex}
+citestyle=numeric]{biblatex}
 \addbibresource{citations.bib}
@@
 \usepackage{graphicx}
-\usepackage{wrapfig,lipsum,booktabs}
+\usepackage{wrapfig,booktabs}
+\usepackage{authblk}
 \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 \title{Capture and Replay Tools in the Field}
-\author{Deepa Chhetri and Brian Pollack}
+\author[1]{Deepa Chhetri}
+\author[1]{Brian Pollack}
+\affil[1]{Department of Electrical Engineering and Computer Science, Case Western Reserve University}
 \maketitle
@@
 They save the time of hand-coding test scripts.
-They also make it simple for testers without significant programming skills to automate their test case \cite{Memom}.
+They also make it simple for testers without significant programming skills to automate their test case \cite{McMaster:2009:EHF:1547559.1548260}.
 However, these tools also have some drawbacks.
-They don’t generate test cases automatically; sometimes the recorded test scripts are inefficient and require manual intervention; the tools know only how to interact with widgets, but they have no idea what application they are operating on \cite{Silverstein}; in regression testing any change in the GUI may cause a test case to break or stop to execute against the updated version \cite{Memom}.\\
+They don’t generate test cases automatically; sometimes the recorded test scripts are inefficient and require manual intervention; the tools know only how to interact with widgets, but they have no idea what application they are operating on \cite{michaelsilverstein2003}; in regression testing any change in the GUI may cause a test case to break or stop to execute against the updated version \cite{McMaster:2009:EHF:1547559.1548260}.\\
 In this paper we compare four capture and replay tools on different criteria.
@@
 \section{Literature Review}
-Nedyalkova and  Bernardino \cite{comparison survey} established a comparison of capture and replay tools.
+Nedyalkova and  Bernardino established a comparison of capture and replay tools.
 They evaluated five open source capture and replay tools namely Abbot, Jacareto, JFCUnit, Marathon and Pounder.
-The criteria that they used for comparison is divided into two major groups - ``General Characteristics'' and ``Capture/Replay Characteristics''.
+The criteria that they used for comparison is divided into two major groups - "General Characteristics'' and "Capture/Replay Characteristics''.
 General characteristics include:
@@
 
-Similarly, Rodrigues et al.\cite{paper 2} performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
+Similarly, Rodrigues et al.
+performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
 They studied the effort required (time spent) to use CR-based and MBT tools.
@@
 
-Mugshot\cite{Mugshot} is a deterministic capture and replay tool developed by Microsoft.
+Mugshot is a deterministic capture and replay tool developed by Microsoft.
 It captures every event that is executed in JavaScript program which can be replayed deterministically at any later time to analyze the sequence of events that might have led to system failure.

### 2017-04-27 paper.tex
Modified section - Extension and Modification of Reanimator. Added placeholders for some future sections.

@@
 \usepackage{authblk}
+\usepackage{hyperref}
 \captionsetup{justification=raggedright,singlelinecheck=false}
@@
 Given tets scripts, the tool can then automatically replay the exact same interactive session any number of times without requiring a human user.
-This helps in early detection of bugs that might lead to system failure and therefore speed up the process of development.\\
+This helps in early detection of bugs that might lead to system failure and therefore speed up the process of development.
+\par
 The advantages of using capture and replay tools is that it saves time by making the process easy and quick.
@@
 However, these tools also have some drawbacks.
-They don’t generate test cases automatically; sometimes the recorded test scripts are inefficient and require manual intervention; the tools know only how to interact with widgets, but they have no idea what application they are operating on \cite{michaelsilverstein2003}; in regression testing any change in the GUI may cause a test case to break or stop to execute against the updated version \cite{McMaster:2009:EHF:1547559.1548260}.\\
+They don’t generate test cases automatically; sometimes the recorded test scripts are inefficient and require manual intervention; the tools know only how to interact with widgets, but they have no idea what application they are operating on \cite{michaelsilverstein2003}; in regression testing any change in the GUI may cause a test case to break or stop to execute against the updated version \cite{McMaster:2009:EHF:1547559.1548260}.
+\par
 In this paper we compare four capture and replay tools on different criteria.
 This comparison study will be helpful for the developers to choose the capture and replay tool that would be best fit for testing their applications.
-Further we extended Reanimator, an existing capture and replay tool, and enhanced it by adding functionality that will help web developers to actually use it in field.\\
+Further we extended Reanimator, an existing capture and replay tool, and enhanced it by adding functionality that will help web developers to actually use it in field.
+\par
 The remainder of this paper is organized as follows.
@@
 It allows tester to replay the test script in a speed that facilitates to observe the actions \cite{Nedyalkova:2013:OSC:2494444.2494464}.
-
+\par
 Similarly, Rodrigues et al.
@@
 They found out that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly \cite{Rodrigues:2014:ECR:2652524.2652587}.
-
+\par
 Mugshot is a deterministic capture and replay tool developed by Microsoft.
@@
 Reanimator demo comes with a tile game.
-We used the same tile game to test Reanimator which is available at 1.eecs493.pollack.tech.\\
+We used the same tile game to test Reanimator which is available at 1.eecs493.pollack.tech.
+\par
 The following criteria are used to establish comparison between these tools:\\ \\
@@
 It does not have any additional feauture.
-\\
+\par
 We modified Reanimator by upgrading it to JQuery 3.2.0 and enabled it to work on Chrome too.
@@
 \section{Extension and Modification of Reanimator}
-We forked the original Reanimator GitHub project at https://github.com/brianmpollack/reanimator.
-It took awhile to determine exactly how the original authors built Reanimator, but we were able to understand their work update their code to work with JQuery 3.2.0, the current version.
+We forked the original Reanimator GitHub project at \href{https://github.com/brianmpollack/reanimator}{https://github.com/brianmpollack/reanimator}.
+It took awhile to determine exactly how the original authors built Reanimator, but we were able to understand their work to determine how Reanimator was built.
+\subsection{Original Reanimator Code}
+Reanimator is built as an extension to JQuery and uses NodeJS to compile the source files.
+The compile scripts start with JQuery and use Almond to inject the Reanimator codebase.
+The main driver of Reanimator is contained in the lib/reanimator/core.js file.
+There is a file in the lib/reanimator/plugins directory which serves as the implementation for each logging feature that Reanimator supports.
 
-While updating the Reanimator code, we learned why it did not initially work in Google Chrome.
+\subsection{Issues with Original Code}
+The original Reanimator code contained a few runtime and compilation issues, which we fixed before continuing to work with Reanimator.
+
+\subsubsection{Google Chrome}
+First, we observed that the precompiled code in the demos did not work in Google Chrome.
 It appears that the original authors tried to convert DOM objects to JSON.
-It is commonly known that JSON does not support circular references, but DOM objects contain numerous circular references.
-Some browsers, such as Firefox, will simply proceed with the JSON encoding and dropped the circular references, but other browsers, such as Chrome, will terminate the JavaScript process.
-We found a simple function that will remove the circular references from the DOM object and convert it to JSON, allowing Reanimator to now be used in any major browser.
-It needs testing on browsers such as Internet Explorer and Edge, but it worked in our preliminary tests with Firefox, Chrome, and Safari.
+DOM stands for Document Object Model and JavaScript uses DOM Objects to represent the webpage contents.
+\par
+It is commonly known that JSON does not support circular references, but DOM Objects contain numerous circular references.
+Some browsers, such as Firefox, will simply proceed with the JSON encoding and will automatically drop the circular references, but other browsers, such as Chrome, will terminate the JavaScript process.
+We found a simple function that will remove the circular references from the DOM object while converting it to JSON, allowing Reanimator to now be used in any major browser (this fixed Reanimator in our tests with Chrome, Firefox, Safari, Internet Explorer, and Edge).
 
+\subsubsection{File Link Error}
 We also found a file error in the included demos.
-The original Makefile added a symbolic link to link the Reanimator JavaScript code to the demos, but the symbolic link caused issues both when all the code is uploaded to GitHub and even locally on my computer.
-For now, we simply copied the correct files into position on our web server, but we plan to update the Makefile to copy the files automatically.
-We are saving this for the end of the project because we anticipate having many changes to make to the demos (to reflect our new features/code), so we will update the demos all at once.
+The original Makefile used a symbolic link to link the Reanimator JavaScript code to the demos, rather than copying the files.
+The symbolic link, however, caused issues both when the code is uploaded to GitHub and even when running locally.
+\par
+We updated the Makefile to copy the files into the demo folders.
+While we could have updated the demo code to link to the dist directory of the Reanimator code, we felt that it was important to allow the demos to be self-contained.
+This would allow a user to copy the contents of a demo folder directly to their server for testing.
+
+\subsection{Uploading Log to Server}
+Originally, Reanimator was not very useful to developers in the field.
+As soon as a user closed his or her browser, any recorded log would be destroyed.
+To make Reanimator more useful to developers, the main feature we wanted to add was log uploading.
+
+\subsubsection{Client Side}
+
+\subsubsection{Server Side}
+
+\section{Future Additions to Reanimator}
+
+\subsection{Developer Interface on Playback}
+
+\subsection{Synchronize Only Changes}
+
+\subsection{Smaller Upload Size}
 
@@
 
-%\bibliographystyle{IEEEtran}
-
 \printbibliography

### 2017-04-27 paper.tex
Added future additions section

@@
 \subsubsection{Client Side}
+We refer to the Reanimator JavaScript code as the client side because it is running locally on the web client’s machine.
+To enable log uploading, we modified the capture function in the core.js file.
+We added parameters so the user could pass in a boolean to enable uploading, and so the client could pass in a UUID to be associated with the log.
+A UUID, or Universally Unique Identifier, is a unique ID for the client.
+Generation and use of UUIDs is outlined in RFC 4122.
+\cite{p.leachm.meallingr.salz2005}
+\par
+The client, if log uploading is enabled, will upload the log to an HTTP POST service every five seconds.
+By default, we programmed Reanimator to POST to a file called reanimator.php in the same directory as the JavaScript file.
+\par
+We duplicated and extended the original tile game demo to support uploading to a webservice.
+A user can play the tile game, then can select a list of sessions from a dropdown.
+After selection, he or she can see any past game that was logged to the server.
 
 \subsubsection{Server Side}
+The server can be written any way the developer prefers as long as it accepts HTTP POST requests.
+\par
+We included a sample HTTP POST web service file in the dist directory of Reanimator.
+The simple script is written in PHP and will upload the logs to a MySQL database for retrieval later.
+It will overwrite any old logs with the same UUID.
+\par
+We also included a sample database configuration file with the uploading tile game demo.
+Because a developer should know how to setup a simple web service and MySQL server, we do not feel the need to explain them in detail.
 
 \section{Future Additions to Reanimator}
+In the future, we recommend adding more features to Reanimator. We believe that it is useful to developers after our additions, but could be improved further.
 
 \subsection{Developer Interface on Playback}
+We propose creating a developer interface, or developer portal.
+It would provide a user friendly way for developers to organize and replay their captured sessions.
+The interface could include a play/pause button, and let the developer choose the speed to play back the session.
+\par
+Because this does not add any core functionality, but rather an improved user experience, we recognize that it would help developers but we did not choose to implement it during our Reanimator extension/proof of usefulness test.
 
 \subsection{Synchronize Only Changes}
+Our demonstration implementation will upload the user's log every five seconds.
+The server code will simply overwrite the log data for that user in the database when it receives new data.
+This practice is fine for demo purposes and for small websites, but is obviously not scalable to large websites.
+We propose uploading only the changes of the log to the server.
+\par
+To ensure that data is not lost, we could allow the server to respond to the POST request to tell the client if the log upload was successful.
+The client would keep track of successful log pushes and would know if it needs to retry or if it can upload a new section of the log.
+\par
+This modification would appear small to each client, but would be a huge difference to large websites which could potentially be receiving many log pushes at the same time.
 
 \subsection{Smaller Upload Size}
+The log files that Reanimator generates are large relative to the usefull information that they contain.
+The files contain every piece of information about the layout of the webpage.
+We propose modifying the way that logs are stored.
+There will be one initial log with the entire DOM, but subsequent events will simply be a changelog of the original log file.
+\par
+This would make the entire log smaller, allowing for smaller uploads and less memory used at the client.
+\par
+It is important to note that this solution is different from the previous suggestion (synchronizing only the changes).
+The entire log would be much smaller, as it would only contain the changes to the original log file.
+We can combine this with the previous suggestion to further minimize the overhead of Reanimator.
 

### 2017-04-27 paper.tex
Formatting and grammatical changes

@@
 
-\IEEEPARstart{S}{oftware} testing is a process of  evaluating the software for its functionality by performing some test cases on an attribute or capability of a program or system and determining that it meets its required results.
-It involves the execution of a software component or system component to evaluate one or more properties of interest.
+\IEEEPARstart{S}{oftware} testing is a process of  evaluating software for its functionality by performing some test cases on an attribute or capability of a program or system and determining that it meets its required results.
+Testing involves the execution of a software component or system component to evaluate one or more properties of interest.
 Testing the graphical user interface (GUI) of a software product is important to ensure the quality of the system and therefore to improve the user experience\cite{Nedyalkova:2013:OSC:2494444.2494464}.
 It not only involves testing the GUI but also the functionality of system.
-But manual testing GUI is tedious and time consuming.
-GUI capture and replay tools was  developed as a mechanism for testing the correctness of interactive applications with graphical user interfaces.
+But manual testing the GUI is tedious and time consuming.
+GUI capture and replay tools were developed as a mechanism for testing the correctness of interactive applications with graphical user interfaces.
 Using a capture and replay tool, a tester can run an application and record the entire interactive session.
@@
 \par
-The advantages of using capture and replay tools is that it saves time by making the process easy and quick.
-They save the time of hand-coding test scripts.
-They also make it simple for testers without significant programming skills to automate their test case \cite{McMaster:2009:EHF:1547559.1548260}.
-However, these tools also have some drawbacks.
-They don’t generate test cases automatically; sometimes the recorded test scripts are inefficient and require manual intervention; the tools know only how to interact with widgets, but they have no idea what application they are operating on \cite{michaelsilverstein2003}; in regression testing any change in the GUI may cause a test case to break or stop to execute against the updated version \cite{McMaster:2009:EHF:1547559.1548260}.
+The advantages of using capture and replay tools include saving time by making the process quicker and easier.
+Capture and replay tools save time by not forcing the developers to hand-code test scripts which would need to be updated each time the application is changed.
+They also make it simple for testers without significant programming skills to automate their test cases \cite{McMaster:2009:EHF:1547559.1548260}.
+This means that companies can hire employees dedicated to testing who are not required to know high level programming, therefore lowering testing costs.
+However, these tools do have some drawbacks.
+They don't generate test cases automatically, sometimes the recorded test scripts are inefficient and require manual intervention, and the tools know only how to interact with widgets, but they have no idea with which application they are operating \cite{michaelsilverstein2003}.
+During regression testing, any change to the GUI may cause a test case to break or stop execution of the updated version \cite{McMaster:2009:EHF:1547559.1548260}.
 \par
-In this paper we compare four capture and replay tools on different criteria.
-This comparison study will be helpful for the developers to choose the capture and replay tool that would be best fit for testing their applications.
-Further we extended Reanimator, an existing capture and replay tool, and enhanced it by adding functionality that will help web developers to actually use it in field.
+In this paper we compare four capture and replay tools using different criteria.
+This comparison study will be beneficial to software developers who want to choose a capture and replay tool which would be a good fit for testing their applications.
+Further we explain how we extended Reanimator, an existing capture and replay tool, and enhanced it by adding functionality that will help web developers effectively run capture and replay tests in the field.
 \par
-The remainder of this paper is organized as follows.
-Section 2 discusses about the previous work done in this field, Section 3 discusses about the tools that were used for the comparison, Section 4 decribes the evaluation criteria used to establish the comparison, Section 5 includes analysis of comparison, Section 6 describes in detail about the extension of Reanimator.
-Finally, in Section 7 we concluded the paper by presenting a short summary.
+The remainder of this paper is organized as follows: Section 2 discusses previous research regarding the comparison of capture and replay tools; Section 3 summarizes each tool that was used for our comparison; Section 4 decribes the evaluation criteria used to establish the comparison; Section 5 describes the results of our analysis; Section 6 describes our modifications to Reanimator; Section 7 contains a summary of our work.
 
@@
 Nedyalkova and Bernardino established a comparison of capture and replay tools.
-They evaluated five open source capture and replay tools namely Abbot, Jacareto, JFCUnit, Marathon and Pounder.
-The criteria that they used for comparison is divided into two major groups - "General Characteristics'' and "Capture/Replay Characteristics''.
+They evaluated five open source capture and replay tools: Abbot, Jacareto, JFCUnit, Marathon, and Pounder.
+The criteria that they used for comparison is divided into two major groups - ``General Characteristics'' and ``Capture/Replay Characteristics''.
 General characteristics include:
@@
 \end{enumerate}
-Based on the results, they found out that Jacareto is the best tool among all five evaluated.
-Jacareto is easy to install, had better documentation, does not require additional programming skills, supports all capture and replay characteristics except for navigation of dialog box.
-It allows tester to replay the test script in a speed that facilitates to observe the actions \cite{Nedyalkova:2013:OSC:2494444.2494464}.
+Based on their analysis, Nedyalkova and Bernardino determined that Jacareto is the best tool among the five they evaluated.
+Jacareto is easy to install, had better documentation, does not require additional programming skills, and supports all capture and replay characteristics except for navigation of dialog box.
+Jacareto allows the tester to speed up or slow down the replay of the application log, helping make testing more efficient \cite{Nedyalkova:2013:OSC:2494444.2494464}.
 \par
@@
 performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
-They studied the effort required (time spent) to use CR-based and MBT tools.
-They compared LoadRunner and Visual Studio CR-based tools and the PLeTsPerf MBT tool to create performance test scripts and scenarios to test web applications.
-LoadRunner (LR) is a performance testing tool based on the CR technique that supports scripts generation and execution to test Web-based applications.
-Visual Studio (VS) [3] is an IDE developed by Microsoft to support software design, development and test.
-PLeTsPerf(PP) is a model-based performance testing tool.
+They studied the effort required (time spent) to use both CR-based and MBT tools.
+They compared LoadRunner and Visual Studio, both CR-based tools, and the PLeTsPerf MBT tool to create performance test scripts and scenarios to test web applications.
+LoadRunner is a performance testing tool based on the CR technique that supports scripts generation and execution to test Web-based applications.
+Visual Studio is an IDE developed by Microsoft to support software design, development and test.
+PLeTsPerf is a model-based performance testing tool.
 Rodrigues et al.
-used used an in-vitro approach, since it refers to the experiment in the laboratory under controlled conditions, addressing a real problem, i.e., the differences in individual effort to create performance test scripts and scenarios using LR,VS and PP.
-They performed the experiment to answer three research questions (RQ) - RQ1.
-What is the effort to generate a single performance test script and scenario using PP, LR, and VS?
-RQ2.
-What is the effort to re-generate performance test scripts and scenarios when using PP, LR, and VS?
-RQ3.
-What is the effort to generate a set of performance test scripts and scenarios using PP, LR, and VS?
+used used an in-vitro approach, since it refers to the experiment in the laboratory under controlled conditions, addressing a real problem, i.e., the differences in individual effort to create performance test scripts and scenarios using LoadRunner,VisualStudio and PLeTsPerf.
+They performed the experiment to answer three research questions:
+\begin{enumerate}
+\item What is the effort to generate a single performance test script and scenario using PLeTsPerf, LoadRunner, and VisualStudio?
+\item What is the effort to re-generate performance test scripts and scenarios when using PLeTsPerf, LoadRunner, and VisualStudio?
+\item What is the effort to generate a set of performance test scripts and scenarios using PLeTsPerf, LoadRunner, and VisualStudio?
+\end{enumerate}
 The experiment execution phase was split into three sessions, each composed of three tasks.
-These tasks were performed using the PP, LR  and VS approaches, one for each task, and all tasks should generate an equivalent performance test script as an output.
-They summarize the result by giving average time spent per treatment to complete each session.
-They found out that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly \cite{Rodrigues:2014:ECR:2652524.2652587}.
+These tasks were performed using the PLeTsPerf, LoadRunner  and VisualStudio approaches, one for each task, and all tasks should generate an equivalent performance test script as an output.
+They summarize the results by giving average time spent per treatment to complete each session.
+They determined that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly \cite{Rodrigues:2014:ECR:2652524.2652587}.
 \par
@@
 \section{Description of Capture and Replay Tools Used}
-In this section, we give a short description of capture and replay tools used in this study.
+In this section, we give a short description of capture and replay tools analyzed in this study.
 We focused on those capture and replay tools that are built for internet applications.
-Here, we compared four tools $-$ Reanimator, Sahi, Telerik and Selenium IDE.
-Following is the description of these tools:
+Here, we compared four tools $-$ Reanimator, Sahi, Telerik and Selenium IDE:
 \subsection{Reanimator}
@@
 Sahi\footnote{http://sahipro.com/} is an Automation testing tool that is used for testing web application.
-There are two versions of Sahi tool: one is open source and is available on SourceForge and proprietary version called Sahi Pro which is available on their official website.
+There are two versions of Sahi tool.
+One is open source and is available on SourceForge.
+The other, named Sahi Pro, is proprietary and is available on their official website.
 It has powerful abilities for recording and replaying across browsers; different language drivers for writing test scripts (Java, Ruby); and support for AJAX and highly dynamic web applications.
@@
 It only supports Windows platform.
-Following figure shows how Sahi fits in a simulated user operation.
+The following figure shows how Sahi fits in a simulated user operation:
 \begin{figure}[h!]
@@
 It has features like visual storyboard and 3D element selection.
-It also offers script-lesstest automation for Silverlight applications.Test Studio offers three product versions:\\
-1. The Functional version performs web and WPF testing and includes the Visual Studio plugin.\\
-2. The Load version performs load testing.\\
-3. The Ultimate version combines Web, Mobile, WPF, Load testing and Test Studio for APIs.\\
+It also offers script-lesstest automation for Silverlight applications.
+Test Studio offers three product versions:
+\begin{enumerate}
+\item The Functional version performs web and WPF testing and includes the Visual Studio plugin.
+\item The Load version performs load testing.
+\item The Ultimate version combines Web, Mobile, WPF, Load testing and Test Studio for APIs.
+\end{enumerate}
 
@@
 \section{Evaluation of Existing Tools}
- The four tools discussed in previous section are installed on an HP laptop with Intel core i5 processor (2.30 GHz), 4 GB RAM and windows 8.1 operating system with Java 1.8.
+The four tools discussed in the previous section were installed on an HP laptop with Intel core i5 processor (2.30 GHz), 4 GB RAM and windows 8.1 operating system with Java 1.8.
 We installed the tools Sahi, Telerik and Selenium.
 The code for Reanimator was directly deployed on a web server we manage.
-Initially, to test these tools (except for Reanimator) a simple online calculator written in Javascript is deployed at 1.eecs493.pollack.tech/index1.html.
-Reanimator demo comes with a tile game.
-We used the same tile game to test Reanimator which is available at 1.eecs493.pollack.tech.
+Initially, to test these tools (except for Reanimator) a simple online calculator written in Javascript was deployed to one of our webservers.
+The demo code for Reanimator comes with a simple puzzle game.
 \par
@@
 
-The modified version of Reanimator is deployed at 2.eecs493.pollack.tech. The developer can select the recorded session to be played from drop down list available.
-Table 1 shows the comparison between Reanimator, Sahi, Telerik  and Selenium based on criteria for evalution for ease of deployment.Table 2 shows the comparison  based on criteria for evalution for level of detail of measurements.Table 3 shows the additiona system information provided with each tool.
+Table 1 shows the comparison between Reanimator, Sahi, Telerik  and Selenium based on criteria for evalution for ease of deployment.
+Table 2 shows the comparison based on criteria for evalution for level of detail of measurements.
+Table 3 shows the additiona system information provided with each tool.
 The symbol \ding{51} means that the tool provides the characteristic which is in evaluation and the symbol \ding{55} means that it doesn’t support it.
@@
 
-%\begin{wraptable}{r}{6.5cm}
 \begin{figure}[h!]
@@
 \section{Comparison Analysis}
-The tools used here does their work of capturing and replaying the interactive sessions.
-But while taking other criteria into consideration, Sahi performs better than the other tools.
+All of the tools we tested are at least functional: they capture interactive web sessions and successfully play them back at a later time.
+While taking all criteria into consideration, Sahi performs better overall than the other tools we tested.
+\par
 Compared to Telerik and Reanimator, Sahi has easier installation.
@@
 \par
-We modified Reanimator by upgrading it to JQuery 3.2.0 and enabled it to work on Chrome too.
-It could be seen that the old version of Reanimator provided by the developers which is available at 1.eecs493.pollack.tech does not work on Chrome.
-While the modified version does work on Chrome.
-Reanimator comes with a demo which is a tile game.
-We have used the same game to test the modified version.
+Later, we talk about modifications we made to Reanimator that make it more functional and easier to use.
+We compared the four tools, however, as we found them directly from their authors.
+We did not compare our upgraded version of Reanimator during this test.
+\par
 Based on the evalution criteria seen in table 1, 2 and 3, we choose Sahi as the best tool among all others.

### 2017-04-28 paper.tex
changes in literature review, figures and summary of changes

@@
 \section{Literature Review}
-Nedyalkova and Bernardino established a comparison of capture and replay tools.
+Nedyalkova and Bernardino \cite{Nedyalkova:2013:OSC:2494444.2494464} established a comparison of capture and replay tools.
 They evaluated five open source capture and replay tools: Abbot, Jacareto, JFCUnit, Marathon, and Pounder.
@@
 Jacareto is easy to install, had better documentation, does not require additional programming skills, and supports all capture and replay characteristics except for navigation of dialog box.
-Jacareto allows the tester to speed up or slow down the replay of the application log, helping make testing more efficient \cite{Nedyalkova:2013:OSC:2494444.2494464}.
+Jacareto allows the tester to speed up or slow down the replay of the application log, helping make testing more efficient .
 \par
 Similarly, Rodrigues et al.
-performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
+\cite{Rodrigues:2014:ECR:2652524.2652587} performed an empirical comparison to evaluate Capture/Replay (CR based) and Model-Based Performance (MBT) testing tools.
 They studied the effort required (time spent) to use both CR-based and MBT tools.
@@
 They summarize the results by giving average time spent per treatment to complete each session.
-They determined that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly \cite{Rodrigues:2014:ECR:2652524.2652587}.
+They determined that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly .
 \par
-Mugshot is a deterministic capture and replay tool developed by Microsoft.
+Mugshot \cite{Mickens:2010:MDC:1855711.1855722} is a deterministic capture and replay tool developed by Microsoft.
 It captures every event that is executed in JavaScript program which can be replayed deterministically at any later time to analyze the sequence of events that might have led to system failure.
@@
 The entry also contains the event type and enough type-specific data to recreate event at play time.
-Mugshot uses a caching proxy to reproduce the load events in the log \cite{Mickens:2010:MDC:1855711.1855722}.
+Mugshot uses a caching proxy to reproduce the load events in the log .
 This is the limitation of Mugshot.
 If an application fetches external contents that does not pass through the proxy, Mugshot cannot guarantee faithful replay of its data or its load time.
+
+\par
+JARDIS \cite{paperA}, a time-traveling debugger for JavaScript.
+It is part of Microsoft’s ChakraCore JavaScript engine and a fork of the Node.js runtime environment .
+The overall system design is a record-replay-snapshot architecture.
+The snapshot algorithm is based on \cite{paperB} with the record-replay work done in the JsRT hosting API layer  that Node.js uses to interface with the JavaScript runtime.
+It provides a rich set of functionality for recording and navigating the execution history of a program including: \\
+
+1.	Local Debuging and Offline Recording :  JARDIS also supports postmortem debugging.
+In this scenario, the developer runs their application under JARDIS’s record mode when deployed to their users, given their consent.
+When an error occurs, the execution trace is sent to the specified location for debugging later.
+The collected trace has sufficient information to replay the execution of the program exactly, including any non-determinism, and show the value of any JavaScript program variable that the developer might be interested in.
+Thus, the debugging experience is the same as if the developer had a debugger attached to the remote Node.js process when the trace was collected.\\
+2.	Reverse-Step Local and Dynamic operations : It allows the developer to step-back in time to the previously executed statement in the current function or to step-back in time to the previously executed statement in any frame including exception throws or callee returns.
+There are two types of reverse-step opertaion.
+The first type of reverse-step operation is a reverse-step (rs) to the previously executed line in the current call frame.
+This is simply the reverse version of the forward step provided by existing graphical and command line debuggers.
+The second type of reverse operation is reverse-step dynamic (rsd) which acts as the reverse version of step-into operations in existing debuggers.This operation steps-back in time to the previously executed statement in any frame.\\
+3.	Reverse to Callback Origin operation : It reverses time to the line that registered the currently executing callback e.g.
+the call to setTimeout where the currently executing function was registered.
 
@@
 Initially, to test these tools (except for Reanimator) a simple online calculator written in Javascript was deployed to one of our webservers.
-The demo code for Reanimator comes with a simple puzzle game.
+The demo code for Reanimator comes with a simple puzzle game that we used for its testing.
 \par
+We divided the criteria on which these tools are to be evaluated in three categories - \\
+1. Evaluation for ease of deployment - In this category, we tried to evaluate the tools on the basis of how easily these tools can be deployed and used redily.\\
+2. Ealuation for level of detail of measurements- In this category, we evaluated the functionality of the tools i.e. what all interactions the tool is capable of capturing.\\
+3. Additional system information - In this category, we provided the additional system information that might be needed by users to choose one of these tools according to their requirement.\\ 
 The following criteria are used to establish comparison between these tools:\\ \\
@@
 
-Table 1 shows the comparison between Reanimator, Sahi, Telerik  and Selenium based on criteria for evalution for ease of deployment.
-Table 2 shows the comparison based on criteria for evalution for level of detail of measurements.
-Table 3 shows the additiona system information provided with each tool.
-The symbol \ding{51} means that the tool provides the characteristic which is in evaluation and the symbol \ding{55} means that it doesn’t support it.
-\\
-
-\begin{figure}[h!]
- \hfill\includegraphics[width=9cm]{figures/table1.PNG}\hspace*{\fill}
-\end{figure}
-\begin{figure}[h!]
- \hfill\includegraphics[width=9cm]{figures/table2.PNG}\hspace*{\fill}
-\end{figure}
-
-\begin{figure}[h!]
- \hfill\includegraphics[width=9cm]{figures/table3.PNG}\hspace*{\fill}
-\end{figure}
-
 \section{Comparison Analysis}
@@
 While taking all criteria into consideration, Sahi performs better overall than the other tools we tested.
+\begin{figure*}[h]
+\centering
+ \hfill\includegraphics[width=10cm]{figures/table1.PNG}\hspace*{\fill}
+\end{figure*}
+\begin{figure*}[h!]
+\centering
+ \hfill\includegraphics[width=10cm]{figures/table2.PNG}\hspace*{\fill}
+\end{figure*}
+
+\begin{figure*}[h!]
+\centering
+ \hfill\includegraphics[width=10cm]{figures/table3.PNG}\hspace*{\fill}
+\end{figure*}
 \par
@@
 This makes the process of analysis cumbersome if the default speed is very fast or slow.
-Telerik has a major setback that its installation takes very long (it took us 1 day to install) to finish since it requires lot of dependencies and also its installation process is not very effective.
+Telerik despite being a great tool has some major issues.The biggest setback of Telerik is that its installation takes very long (it took us 1 day to install) to finish since it requires lot of dependencies and also its installation process is not very effective.
 It requires large hard disk space.
 It has the feature called visual storyboard which gives the snapshot of each scenario recorded by tool.
-This allows the developer to go to any snapshot.
+This allows the developer to go to any snapshot to analyse the interaction.
 We used the one month free trial version of Telerik and requires to purchase once the trial period expires.
 Telerik also supports Chrome, Firefox and Internet Explorer.
-Reanimator is a small capture and replay tool inspired by Mugshot.
-It requires programming skills since it does not come as ready to use testing tool.
+Reanimator is a very basic capture and replay tool inspired by Mugshot.
+It requires programming skills to get it working since it does not come as ready to use testing tool.
 It is built on JQuery 1.8.3.
-It requires programming skills to get Reanimator working.Also it works only on Firefox and Internet Explorer.
-It does not have any additional feauture.
+Also it works only on Firefox and Internet Explorer.
+It does not have any additional feauture like the other tools.
 \par
-Later, we talk about modifications we made to Reanimator that make it more functional and easier to use.
+Later, we talk about modifications we made to Reanimator that made it more functional and easier to use.
 We compared the four tools, however, as we found them directly from their authors.
@@
 \par
+Table 1 shows the comparison between Reanimator, Sahi, Telerik  and Selenium based on criteria for evalution for ease of deployment.
+Table 2 shows the comparison based on criteria for evalution for level of detail of measurements.
+Table 3 shows the additional system information provided with each tool.
+The symbol \ding{51} means that the tool provides the characteristic which is in evaluation and the symbol \ding{55} means that it doesn’t support it.
+\\
 Based on the evalution criteria seen in table 1, 2 and 3, we choose Sahi as the best tool among all others.
@@
 
+\section{Summary of Changes}
+We expanded our study of previous work done in the field of capture and replay.
+We studied "Time Travel Debugging for Javascript/Node.js".
+This is one of the latest work in this field that allows a developer to simply press a button to step-back in a program’s execution without having developer to manually stop debugging, set a new breakpoint, and then reproduce the desired execution to hit that breakpoint.
+
 \printbibliography

### 2017-04-28 paper.tex
Added citations from Deepa

@@
 \par
-JARDIS \cite{paperA}, a time-traveling debugger for JavaScript.
+JARDIS \cite{time-travel-debugging-javascriptnode-js}, a time-traveling debugger for JavaScript.
 It is part of Microsoft’s ChakraCore JavaScript engine and a fork of the Node.js runtime environment .
 The overall system design is a record-replay-snapshot architecture.
-The snapshot algorithm is based on \cite{paperB} with the record-replay work done in the JsRT hosting API layer  that Node.js uses to interface with the JavaScript runtime.
+The snapshot algorithm is based on \cite{Barr:2014:TAT:2714064.2660209} with the record-replay work done in the JsRT hosting API layer  that Node.js uses to interface with the JavaScript runtime.
 It provides a rich set of functionality for recording and navigating the execution history of a program including: \\

### 2017-04-28 paper.tex
Minor changes from proofreading, extended summary of changes, extended conclusion

--- 2017-04-28 paper.tex
@@
 Jacareto is easy to install, had better documentation, does not require additional programming skills, and supports all capture and replay characteristics except for navigation of dialog box.
-Jacareto allows the tester to speed up or slow down the replay of the application log, helping make testing more efficient .
+Jacareto allows the tester to speed up or slow down the replay of the application log, helping make testing more efficient.
 \par
@@
 They summarize the results by giving average time spent per treatment to complete each session.
-They determined that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly .
+They determined that for simple testing tasks the effort of using CR-based tool was less than MBT tool but as the complexity of testing task increases the advantage of using MBT grows significantly.
 \par
@@
 The entry also contains the event type and enough type-specific data to recreate event at play time.
-Mugshot uses a caching proxy to reproduce the load events in the log .
+Mugshot uses a caching proxy to reproduce the load events in the log.
 This is the limitation of Mugshot.
@@
 \par
-JARDIS \cite{paperA}, a time-traveling debugger for JavaScript.
-It is part of Microsoft’s ChakraCore JavaScript engine and a fork of the Node.js runtime environment .
+Microsoft calls JARDIS a ``time-traveling'' debugger for JavaScript.
+It is part of their ChakraCore JavaScript engine and a fork of the Node.js runtime environment \cite{time-travel-debugging-javascriptnode-js}.
 The overall system design is a record-replay-snapshot architecture.
-The snapshot algorithm is based on \cite{paperB} with the record-replay work done in the JsRT hosting API layer  that Node.js uses to interface with the JavaScript runtime.
+The snapshot algorithm is based on a tool called Tardis with the record-replay work done in the JsRT hosting API layer that Node.js uses to interface with the JavaScript runtime \cite{Barr:2014:TAT:2714064.2660209}.
 It provides a rich set of functionality for recording and navigating the execution history of a program including: \\
@@
 \section{Conclusion}
-In our study, we compared four capture and replay tools, namely Reanimator, Sahi, Telerik and Selenium.
-The goal of this study was to determine the best tool among these which has best overall performance.
-These tools were compared on different criteria to find out which tool has reliable capture and replay capabilities without requiring too much human efforts.
-After evaluating each one of the tools, we came to a conclusion that the tool that best satisfies our requirements is Sahi.
-This tool stood out from rest of the tools as it has best overall performance.
-Therefore, we can say that Sahi can be easily adapted by any developer to test their GUI application.
-We also worked on Reanimator to enhance it by additing new functionalities to it.
-We enabled it to work on Chrome.
-We ...{to be added by Brian}
+\subsection{Tool Comparison}
+In our study, we compared four capture and replay tools: Reanimator, Sahi, Telerik, and Selenium.
+The goal of our study was to determine the best tool among these four for a developer to use in the field.
+We compared the four tools on different criteria to find out which tool has reliable capture and replay capabilities without requiring too much time to set up and use.
+\par
+After evaluating all four tools, we came to the conclusion that Sahi best satisfies our requirements.
+We believe that Sahi has the best overall performance and can be easily adapted by any developer to test their GUI application.
+\subsection{Reanimator Extension}
+We modified Reanimator with the expectation that it would be more useful for JavaScript developers to deploy to their applications in the field.
+We fixed bugs present in the original code to make Reanimator compatable with Google Chrome, upgraded it to support JQuery 3.2.0, and extended the functionality to allow developers to request the logs be uploaded to a server.
+\par
+Because the original code for Reanimator has not been modified in four years, we assumed that the developers abandoned the project.
+Because our version was siginificantly different from the original, we decided to not issue a pull request back to the original codebase.
+\par
+We believe that the original version of Reanimator was novel, but not very useful because the log was lost when a user exited his or her browser.
+With the addition of persistent logs (if they are being uploaded to a server), we believe that Reanimator is a very solid, lightweight capture and replay tool.
+We recommend that JavaScript developers implement it if they need to capture logs.
+\par
+We recommend adding a few more featurers to Reanimator. We recommend making the log filesizes smaller and adding a user interface for developers to help them navigate through a user's session.
 
 \section{Summary of Changes}
-We expanded our study of previous work done in the field of capture and replay.
-We studied "Time Travel Debugging for Javascript/Node.js".
-This is one of the latest work in this field that allows a developer to simply press a button to step-back in a program’s execution without having developer to manually stop debugging, set a new breakpoint, and then reproduce the desired execution to hit that breakpoint.
+\subsection{Tool Comparison}
+Before our initial progress report, we had already made great progress with our analysis of different capture and replay tools.
+We wanted to perform the analysis early so that we could focus on the extension to Reanimator, which we viewed as the more important part of this project, since it involved creating new features that would be useful to developers.
+\par
+Since our initial progress report, we expanded our study of previous work done in the field of capture and replay by studying ``Time Travel Debugging for Javascript/Node.js''.
+This is one of the more recently developed tools in the field that allows a developer to simply press a button to step-back in a program's execution without requiring the developer to manually stop debugging, set a new breakpoint, and then reproduce the desired execution to hit that breakpoint.
+We were impressed with this tool.
+\subsection{Reanimator Extension}
+At the time of our initial progress report, we had upgraded Reanimator to work with JQuery 3.2.0.
+We also fixed the bugs in the code which prevented Google Chrome users from recording a session.
+We had to spend a significant amount of time learning how the original authors compiled the original version of Reanimator, since they left out a few important dependencies in the package.json dependency list.
+\par
+Since our initial progress report, we have implemented and tested the upload feature of Reanimator. We also built a new demo page to showcase the new feature.
 

### 2017-04-28 paper.tex
Updated abstract and title

@@
 \title{Capture and Replay Tools in the Field}
-\author[1]{Deepa Chhetri}
-\author[1]{Brian Pollack}
-\affil[1]{Department of Electrical Engineering and Computer Science, Case Western Reserve University}
+%\author[1]{Deepa Chhetri}
+%\author[1]{Brian Pollack}
+%\affil[1]{Department of Electrical Engineering and Computer Science\\Case Western Reserve University\\Cleveland, OH 44106}
+
+\author{\IEEEauthorblockN{Deepa Chhetri\IEEEauthorrefmark{1}, Brian Pollack\IEEEauthorrefmark{2}}\\
+\IEEEauthorblockA{Department of Electrical Engineering and Computer Science\\Case Western Reserve University\\Cleveland, OH 44106\\\IEEEauthorrefmark{1}dxc496@case.edu, \IEEEauthorrefmark{2}bmp55@case.edu}
+}
+
 \maketitle
@@
 \begin{abstract}
-In GUI applications, a user interacts with the system via graphical interface such as mouse click, scroll, drag, text box etc.
-There could be large number of possible sequences in which a user can interact.
-Testing such application means ensuring the correct sequence of interactions resulting in desired output.
-If this testing is done manually, it could be tedious.
-Therefore, capture and replay tools came into existence.
-It  enables the testers to record the entire ineteractive session and replaying it at any later time.
-By replaying a given log file on a changed version of the application, capture and replay tools thus support fully-automatic regression testing of graphical user interfaces.
+We compared four different capture and replay tools, mainly based on their performance and ease of use.
+We compared Reanimator, Sahi, Telerik, and Selenium IDE and determined that Sahi is overall the best capture and replay tool.
+Additionally, we extended Reanimator to fix core bugs, upgrade it to support JQuery 3.2.0 (the current version at time of writing), and enable it to upload its captures to a server.
+We believe that our extended version of Reanimator is now useful to JavaScript developers and can conveniently be used in the field.
 \end{abstract}
